---
title: "compareScenarios2"
author: "Christof Schötz"
date: "2022-01-10"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{compareScenarios2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```

# Structure and Main Features

The function `compareScenarios2()` of the `remind2` package can be used to visually compare the results of multiple runs of the IAM REMIND. 

The function reads the results from the output-mif-files (in the remind folder after runs are completed, the files `output/<scenario_folder>/REMIND_generic_<scenario>.mif`). Additionally it reads historical data from a `historical.mif` in one of the scenario output folders. Using this data, a report containing many plots is created and written as a PDF- or HTML-file. See `?remind2::compareScenarios2` for information on how to call the function with the appropieate argumens.

Internally, `compareScenarios2()` calls `rmarkdown::render()` on certain Rmarkdown-files (Rmd-files). Rmd-files may contain R-code (e.g., for creating plots) as well as descriptive text (in this case, mostly section titles). The Rmd-files to be rendered are part of the remind2-package. In the development state of the package, they can be found in the folder `inst/markdown/compareScenarios2/`. 
To be more precises, `rmarkdown::render()` is called on `cs2_main.Rmd` in this folder, which includes other Rmd-files - one for each section of the output document.
The loading and preprocessing of data happens in `cs2_main.Rmd`; the section Rmd-files mostly call plot-functions. The plot-functions are contained in `cs2_plot_functions.R`.

Aside from HTML- and PDF-documents as output, `compareScenarios2()` also allows to obtain a copy of the Rmd-files needed to create these outputs (by setting the argument `outputFormat = "Rmd"`). Rendering the resulting Rmd-files to PDF or HTML yields the same documents as calls to `compareScenarios2()` with `outputFormat = "PDF"` or `"HTML"`. The advantage of being able to access these Rmd-files is the possibility to change the plotting code without changing the code of the `remind2`-package. Moreover, Rmd-files can be used interactively in RStudio: 

## Interactive Use of the Rmd-files

The code in these files is structured in chunks and each chunk can be run separately by clicking on its play-button. Typically, one would call `compareScenarios2()` with `outputFormat = "Rmd"`, then open the file `cs2_main.Rmd`. At the end of the file, there is a chunk
````
```{r prepare mark}
# CLICK "RUN ALL RUNS ABOVE" HERE TO PREPARE YOUR ENVIRONMENT
```
```` 
Clicking on the *triangle above bar*-button on the right executes all chunks above and by that loads and prepares the data for plotting. After that one can open any section-Rmd-file and execute a chunk to create the respective plots. The plots should appear in RStudio inside the Rmd-file below the chunk.

## YAML-header

The file `cs2_main.Rmd` starts with a YAML header marked by `---`. This header declares some basic information of the report, like its title and the output format. Furthermore, it contains a list `params`, which parameterizes the report. Among others, such parameters are the paths to the mif-files and certain properties that are shared for all plots in the report. Each such parameter can be changed by a respective argument in the call of `compareScenarios2()`.

## cs2_main.Rmd

This file loads the data from the mif-files, preprocesses the data, and at the very end includes the section-Rmd-files (and optionally further Rmd-files provided by the user).


### Loading

The mif-files are loaded using `quitte::read.quitte()`. This function names the global region `"World"` (not `"GLO"` as `magclass::read.report()`). For each file, we obtain one data-frame with columns `model, scenario, region, variable, unit, period, value`. During preprocessing the data-frames are concatenated into one with variable name `data`. Furthermore, a column `gdp` is added during preprocessing to make it easier to create plots with GDP per capita on the horizontal axis.
In the sections, `data` is used to provide the data necessary for the plots.

### Preprocessing

* Scenarios are renamed if the user specifies new names (using a named vector for the argument `mifScen` of `compareScenarios2()` or by setting the parameter `mifScenNames` in the Rmd-files).
* The columns `period` (years) and `region` are filtered according to the parameters `yearsScen`, `yearsHist`, and `reg`.
* In the historical data, if all values of the same model, scenario, variable and region are 0, these rows are removed.
* `|+|, |++|, |+++|, ...` are removed from variable names.
* Optionally, for some scenario-variable combinations, the models in the data can be filtered (mostly for historical data, i.e., `scenario == "historical"`, that provides multiple models for the same variable).
* For a specified list of variables, a new per-capita-variable is created with the name `"<OLD_NAME> pCap"`.
* `"GDP|PPP pCap"` is added as a new column `gdp` of `data` to make it easier to create plots with GDP per capita on the horizontal axis.
* For a specified list of variables, a new per-GDP-variable is created with the name `"<OLD_NAME> pGDP"`. As the denominator, the value of `GDP|PPP pCap` is used.

### Global Variables 

Global variables are created in `cs2_main.Rmd` and are intended to be used in the plot functions of the section-Rmd-files.

* `data`: a data-frame with columns `model, scenario, region, variable, unit, period, value, gdp` that provides all data that may be plotted.
* `variables`: a character vector containing the set of all variables in `data`.
* `regions`: a character vector containing the set of all regions in `data`.
* `mainReg`: a single character string with the name of the main region, which is shown in larger plots for some plot functions. Usually `"World"`.
* `yearsBarPlot`: a numeric vector containing the years to be plotted in bar plots.

## cs2_plot_functions.R

This R-script is sourced in `cs2_main.Rmd` and contains functions that make it simple to create the standard plots regularly used in the compareScenarios-output.

Again, these functions are not functions of the package, but a sourced R-script. This has the effect, that the functions can refer to the 'global variables' mentioned above. Furthermore, the `cs2_plot_functions.R` is copied when calling `compareScenarios2()` with `outputFormat="Rmd"`, which makes is easier for users to modify.

The plot functions do not return a plot object, but draw the plot or multiple plots directly.

To modify plots, it is recommended to copy the body of the respective plot function (e.g., to a new chunk) and modify this code.

## Section-Rmd-files

The section-Rmd-files follow the naming pattern `cs2_NN_XXXX.Rmd`, where `NN` is replaced by a two digit number and `XXXX` is replaced by a short name of the section. If the YAML-parameter `sections` is set to `"all"`, the default, all sections of this naming pattern are included in `cs2_main.Rmd`. Alternatively, `sections` can be set to a vector of individual sections in the form of `"NN_XXXX"` to only render these sections.

The section-Rmd-files consist of section and sub-section titles, marked by `#`, `##`, `###`, ..., and R-code chunks which create plots, usually by calling one of the plot-functions of `cs2_plot_functions.R`.


# Further Notes

## Ordering in the Plots

By default the variables in area-plots are ordered by average area, such that the variable with the largest average area is at the bottom.
This is done by a call of the following form inside the respective plot functions before the call of `mipArea(d)`.

```{r}
data %>% 
  mutate(variable = fct_reorder(variable, value, mean, na.rm=TRUE)) ->
  d
```

Other possibilities are:

```{r}
# order as given in items
data %>% 
  mutate(variable = fct_relevel(variable, items)) -> 
  d

# order by value in first year
data %>% 
  mutate(variable = fct_reorder2(variable, period, value, first2, .desc=FALSE)) -> 
  d
```

## userSectionPath

The user can provide one or more additional Rmd-files that are appended after the sections provided by the package. Setting `sections` to `NULL` and `userSectionPath` to a character-vector of paths to Rmd-files creates a fully user-defined report.

