---
title: "compareScenarios2"
author: "Christof Schötz"
date: "2022-02-28"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{compareScenarios2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```


The function `compareScenarios2()` of the `remind2` package can be used to visually compare the results of multiple runs of the IAM REMIND. 

The function reads the results from the output-mif-files (in the remind folder after runs are completed, the files `output/<scenario_folder>/REMIND_generic_<scenario>.mif`). Additionally it reads historical data from a `historical.mif` in one of the scenario output folders. Using this data, a report containing many plots is created and written as a PDF- or HTML-file. See `?remind2::compareScenarios2` for information on how to call the function with the appropriate arguments.

Internally, `compareScenarios2()` calls `rmarkdown::render()` on certain Rmarkdown-files (Rmd-files). Rmd-files may contain R-code (e.g., for creating plots) as well as descriptive text (in this case, mostly section titles). The Rmd-files to be rendered are part of the remind2-package. In the development state of the package, they can be found in the folder `inst/markdown/compareScenarios2/`. 
To be more precises, `rmarkdown::render()` is called on `cs2_main.Rmd` in this folder, which includes other Rmd-files - one for each section of the output document.
The loading and preprocessing of data happens in `cs2_main.Rmd`; the section Rmd-files mostly call plot functions.

Aside from HTML- and PDF-documents as output, `compareScenarios2()` also allows to obtain a copy of the Rmd-files needed to create these outputs (by setting the argument `outputFormat = "Rmd"`). Rendering the resulting Rmd-files to PDF or HTML yields the same documents as calls to `compareScenarios2()` with `outputFormat = "PDF"` or `"HTML"`. The advantage of being able to access these Rmd-files is the possibility to change the plotting code without changing the code of the `remind2`-package. Moreover, Rmd-files can be used interactively in RStudio.

# Local Use and mif-Files

`compareScenarios2()` with default settings can be called automatically after a bundle of runs on the cluster has finished or manually via `Rscript output.R`. It can also be called directly as a function of the R-package `remind2`, e.g.,

```{r}
library(remind2)
compareScenarios2(
  mifScen = c("path/to/Base.mif", "path/to/NDC.mif"),
  mifHist = "path/to/historical.mif",
  outputFile = "CompareScenarios2Example")
```

To do this locally on our own computer, we need some mif files. One possiblity is to adapt and execute the following script to download the newest *modeltest* files.

```{r eval=FALSE}
library(tidyverse)
library(ssh)

# TODO: Adapt the following three lines!
keyfile <- "path/to/ssh/private/key/.ssh/id_rsa"
username <- "username"
out_path <- "path/to/where/mifs/will/be/downloaded/"

# path on the cluster where to search for mifs:
path <- "/p/projects/remind/modeltests/output/" 

# Connect to the cluster and get the file names of the newest modeltest mifs.
session <- ssh_connect(paste0(username, "@cluster.pik-potsdam.de"), keyfile=keyfile)
out <- ssh_exec_internal(session, paste("ls", path))
out$stdout %>%
  rawToChar() %>%
  str_split("\n", simplify = TRUE) %>%
  str_subset("^[a-zA-Z0-9-]+_\\d{4}-\\d{2}-\\d{2}_\\d{2}\\.\\d{2}\\.\\d{2}$") ->
  filenames
filenames %>%
  str_split("_", simplify = TRUE) %>%
  matrix(ncol=3, dimnames=list(NULL, c("name", "date", "time"))) %>%
  as_tibble() %>%
  bind_cols(filename = filenames) %>%
  mutate(date = as.Date(date)) %>%
  filter(date >= max(date)-2) ->
  new_file_data

new_files <- paste0(path, new_file_data$filename, "/REMIND_generic_", new_file_data$name, ".mif")
walk(new_files, scp_download, session = session, to = out_path) # download scenario mifs

hist_path <- paste0(path, new_file_data$filename[1], "/historical.mif") 
scp_download(session = session, hist_path, to = out_path) # download historical.mif

ssh_disconnect(session)
```


# Interactive Use of the Rmd-files

In this section, we assume that we do not want to change the package `remind2`. But we may want to make changes to the compareScenarios output locally.

We call `remind2::compareScenarios2()` with `outputFormat = "Rmd"` to obtain a (modified) copy of the Rmd-files.

```{r eval=FALSE}
library(remind2)
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif", "path/to/scen3.mif"), # TODO.
  mifHist = "path/to/historical.mif", # TODO.
  outputDir = "path/to/where/rmds/should/be/copied/to", # TODO.
  outputFormat = "Rmd",
  # Add current time as output name to not overwrite other things:
  outputFile = format(Sys.time(), "CompScen2-%Y%m%d-%H%M%S")) 
```

The code in these Rmd-files is structured in chunks and each chunk can be run separately by clicking on its play-button. We first open `cs2_main.Rmd`. At the end of the file, there is a chunk
````
```{r prepare mark}
# CLICK "RUN ALL CHUNKS ABOVE" HERE TO PREPARE THE ENVIRONMENT
```
```` 
Clicking on the *triangle above bar*-button on the right executes all chunks above and by that loads and prepares the data for plotting. After that one can open any section-Rmd-file and execute a chunk to create the respective plots. The plots should appear in RStudio inside the Rmd-file below the chunk.

# Workflow for Adding a new Plot to CompareScenarios2

1. If not done already, fork <https://github.com/pik-piam/remind2>.
2. In your personal github remind2 repository, create a new branch.
3. Clone the repository and switch to the newly created branch to get your local copy.
4. In your local copy, open `remind2.Rproj` in RStudio.
5. Press `CTRL+SHIFT+L` to call `devtools::load_all(".")`, which loads `remind2` from your local copy.
6. Assuming you have some mifs available for testing, call

```{r eval=FALSE}
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif"), # TODO.
  mifHist = "path/to/historical.mif", # TODO.
  outputFile = format(Sys.time(), "CompScen2-%Y%m%d-%H%M%S"),
  sections = NULL,
  envir = globalenv())
```

This executes the code in `cs2_main.Rmd` without creating any plots. This will take some seconds, but it should not take minutes. Type `data` into the RStudio console and hit enter. This should show you the first rows of a table that contains all the loaded data.

7. Open the section file in which you want to add the plot. The files are in the folder `inst/markdown/compareScenarios2/` and have names of the form `c2_NN_XXXX.Rmd`, where `NN` is a two digit number and `XXXX` is resembles the section title.
8. You should be able to execute any chunk in the section Rmd by clicking the play button in its top right corner.
9. Insert a new chunk by copying an old one or by pressing `CTRK+ALT+I`.
10. Add a new plot inside the chunk, e.g., `showLinePlots(data, "Your|Variable|Name")`. See the section *Plot Functions* below.
11. Run your newly created chunk to see the plot.
12. Run the following code to see your new plot in a PDF.

```{r eval=FALSE}
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif"), # TODO.
  mifHist = "path/to/historical.mif", # TODO.
  outputFile = format(Sys.time(), "CompScen2-%Y%m%d-%H%M%S"),
  outputFormat = "PDF", # PDF is the default, so you can leave that line out. Or change it to html to get a html-version.
  sections = <NN>) # TODO: Replace <NN> by the number of the section you changed (or by "all" to build the whole compare scenarios file, which will take a while)
```

13. Save the file. Commit your changes. In the commit message, you may use the shorthand `cs2` to indicate that you made a change to compareScenarios2, e.g., `cs2: added plot of My|Variable`.
14. Make sure you fetched and pulled all recent changes to remind2. Then, call `lucode2::buildLibrary()`. Commit again with the commit message `` `lucode2::buildLibrary()` ``. Push your commits to github.
15. Create a pull request.

# cs2_main.Rmd

This file loads the data from the mif-files, preprocesses the data, and includes the section-Rmd-files at the very end (and optionally further Rmd-files provided by the user, see YAML-parameter `userSectionPath`).

## YAML-header

The file `cs2_main.Rmd` starts with a YAML header marked by `---`. This header declares some basic information of the report, like its title and the output format. Furthermore, it contains a list `params`, which parameterizes the report. Among others, such parameters are the paths to the mif-files and certain properties that are shared for all plots in the report. Each such parameter can be changed by a respective argument in the call of `compareScenarios2()`, see section *YAML Parameters* in the documentation of the function.

## Loading

The mif-files are loaded using `quitte::read.quitte()`. This function names the global region `"World"` (not `"GLO"` as `magclass::read.report()`). For each file, we obtain one data-frame with columns `model, scenario, region, variable, unit, period, value`. During preprocessing the data-frames are concatenated into one quitte object named `data`. In the sections, `data` is used to provide the data necessary for the plots.

## Preprocessing

* Scenarios are renamed if the user specifies new names (using a named vector for the argument `mifScen` of `compareScenarios2()` or by setting the parameter `mifScenNames` in the Rmd-files).
* The columns `period` (years) and `region` are filtered according to the parameters `yearsScen`, `yearsHist`, and `reg`.
* `|+|, |++|, |+++|, ...` are removed from variable names. An additional column `varplus` is added to the data frame, which retains the original name including `+`. This column is used by `mip::showAreaAndBarPlotsPlus()`.
* For a specified list of variables, a new per-capita-variable is created with the name `"<OLD_NAME> pCap"`.
* For a specified list of variables, a new per-GDP-variable is created with the name `"<OLD_NAME> pGDP"`. As the denominator, the value of `GDP|PPP pCap` is used.

## Global Variables 

Global variables are created in `cs2_main.Rmd` and are intended to be used in the plot functions of the section-Rmd-files.

The quitte-object (data frame) `data` with columns `model, scenario, region, variable, unit, period, value, varplus` provides all data that may be plotted.
It has mostly factor-columns. Thus, a vector of all available regions can be obtained by `levels(data$region)`.

Some arguments of the `mip::show...()` plot functions use the functionality provided by the base-R functions `options()` and `getOption()`. In `cs2_main.Rmd` there are calls to `options()`, setting values of the global options `mip.mainReg`, `mip.yearsBarPlot`, and `mip.histRefModel`. The plotting functions may have an argument, e.g., `mainReg` with default value `getOption("mip.mainReg")`. Thus, this argument does not have to be stated for each call of the plot function (assuming the respective call of `options()` sets it to the right value).

# Section-Rmd-files

The section-Rmd-files follow the naming pattern `cs2_NN_XXXX.Rmd`, where `NN` is replaced by a two digit number and `XXXX` is replaced by a short name of the section. If the YAML-parameter `sections` is set to `"all"`, the default, all sections of this naming pattern are included in `cs2_main.Rmd`. Alternatively, `sections` can be set to a vector of individual sections in the form of `"NN_XXXX"` to only render these sections.

The section-Rmd-files consist of section and sub-section titles, marked by `#`, `##`, `###`, ..., and R-code chunks which create plots, usually by calling one of the `show...()`-functions in the `mip` package.

## userSectionPath

The user can provide one or more additional Rmd-files that are appended after the sections provided by the package. Setting `sections` to `NULL` and `userSectionPath` to a character-vector of paths to Rmd-files creates a fully user-defined report.


# Plot Functions

The section Rmd-files mostly consist of simple calls of a `show...()`-function from the the [mip](https://github.com/pik-piam/mip) package. These functions are designed to make the creation of re-occurring kinds of plots in comapreSceanrios2 simple. Alternatively, one can build custom plots using `ggplot2`.

The `mip`-package contains following default plot functions for comapareScenarios2: 

* `showAreaAndBarPlots()`
* `showAreaAndBarPlotsPlus()`
* `showLinePlots()`
* `showLinePlotsWithTarget()`
* `showMultiLinePlots`
* `showMultiLinePlotsByVariable()`
* `showRegiLinePlots()`

All but `showLinePlotsWithTarget()` can use the global option `mip.mainReg`.
`showAreaAndBarPlots()` and `showAreaAndBarPlotsPlus()` can use `mip.yearsBarPlot`.
`showMultiLinePlotsByVariable()` uses `mip.histRefModel`.

See the respective function documentation for more information and example plots.

## Ordering in the Area-Plots

By default the variables in area-plots are ordered by average area, such that the variable with the largest average area is at the bottom.

