---
title: "compareScenarios2"
author: "Christof Schötz"
date: "2022-03-11"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{compareScenarios2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Overview

The function `compareScenarios2()` (*cs2* for short) of the `remind2` package can be used to visually compare the results of multiple runs of the IAM [REMIND](https://github.com/remindmodel/remind) 

It can be called via the [`remind/output.R`](https://github.com/remindmodel/remind/blob/develop/output.R) script: Execute `Rscript output.R` in the REMIND folder, select `Comparison across runs` and then `compareScenarios2`.

The function reads the results from the output-mif-files (in the remind folder after runs are completed, i.e., the files `./output/<run_folder>/REMIND_generic_<run>.mif`). Additionally it reads historical data from a `historical.mif` in one of the run output folders. Using this data, a document containing many plots is created and written as a PDF- or HTML-file. See `?remind2::compareScenarios2` for information on how to call the function directly with the appropriate arguments.

Internally, `compareScenarios2()` calls `rmarkdown::render()` on certain Rmarkdown-files (Rmd-files). Rmd-files may contain R-code (e.g., for creating plots, creating tables) as well as descriptive text (in this case, mostly section titles). The main Rmd-files to be rendered are part of the remind2-package. Some optional section may be placed in the REMIND repository at [`remind/scripts/cs2/`](https://github.com/remindmodel/remind/tree/develop/scripts/cs2). In the development state of the package, the main Rmd-files can be found in the folder [`remind2/inst/markdown/compareScenarios2/`](https://github.com/pik-piam/remind2/tree/master/inst/markdown/compareScenarios2). 
To be more precises, `rmarkdown::render()` is called on `cs2_main.Rmd` in this folder, which includes other Rmd-files - one for each section of the output document.
The loading and preprocessing of data happens in `cs2_main.Rmd`; the section Rmd-files mostly call plot functions.

Aside from HTML- and PDF-documents as output, `compareScenarios2()` also allows to obtain a copy of the Rmd-files needed to create these outputs (by setting the argument `outputFormat = "Rmd"`). Rendering the resulting Rmd-files to PDF or HTML yields the same documents as calls to `compareScenarios2()` with `outputFormat = "PDF"` or `"HTML"`. The advantage of being able to access these Rmd-files is the possibility to change the plotting code without changing the code of the `remind2`-package. Moreover, Rmd-files can be used interactively in RStudio.

# Usage

`compareScenarios2()` with different predefined settings can be called via `Rscript output.R`. It can also be called directly as a function of the R-package `remind2`.

## output.R and Profiles

### output.R

Typically we want to compare the results of some REMIND runs which were created in the `remind/output/` folder of a clone of the REMIND repository. Assume such runs are available and, in particular, the `remind/output/<run_folder>/REMIND_generic_<run>.mif` of the runs of interest exist. Go to the REMIND directory `remind/` and call `Rscript output.R`. Then choose `Comparison across runs` and `compareScenarios2`. Select the runs of interest. We then can choose a filename prefix for the output file if we want. Next, choose a slurm mode, e.g., `short` (the job will run for less than 1 hour, usually something like 20min). Finally we can choose a cs2-profile. Standard profiles for the selected runs are colored. After choosing one or more profiles, the respective slurm jobs will be started. An HTML- or PDF-file will be created. If something goes wrong, take a look at the `*.log`-file with the same name as the cs2-output file.

### Profiles

A cs2-profile is a set of arguments for `compareScenarios2()`. There are different profiles for a comparison on the 12 main REMIND regions (`H12`, `H12-short`), or on the European regions (`EU27`, `EU27-short`) for 21-region-runs. The suffix `-short` indicates that only periods up to 2050 are considered. The `default`-profiles just call `compareScenarios2()` with the default arguments as described in `?remind2::compareScenarios2`.
The available profiles are stored in [`remind/scripts/cs2/profiles.json`](https://github.com/remindmodel/remind/blob/develop/scripts/cs2/profiles.json). Take a look at this file (open in text editor) to see the definition of each profile.

### Changing or Adding Profiles

To change a profile or add a new profile, just edit [`remind/scripts/cs2/profiles.json`](https://github.com/remindmodel/remind/blob/develop/scripts/cs2/profiles.json). Read the `_DESCRIPTION_` in that file. Every argument (including YAML-arguments) to `compareScenarios2()` can be set or changed. 

We can create our own cs2-report:
First we create an "section"-Rmd-file, similar to `cs2_NN_XXXX.Rmd` in [`remind2/inst/markdown/compareScenarios2`](https://github.com/pik-piam/remind2/tree/master/inst/markdown/compareScenarios2). It typically contains calls to plot-function using an R-object called `data`. This objects stores all the information read from the mif-files. We place our "section"-Rmd-file in [`remind/scripts/cs2/`](https://github.com/remindmodel/remind/tree/develop/scripts/cs2). Then we add a new profile in [`remind/scripts/cs2/profiles.json`](https://github.com/remindmodel/remind/blob/develop/scripts/cs2/profiles.json) with options `"sections": "0"` and `"userSectionPath": "normalizePath('./scripts/cs2/ourSection.Rmd')"`. The new profile should appear as a choice in the `output.R`-dialog. Choosing it will create a cs2-report consisiting only of the Info-section and our own section. See the profile `mySection` and [`remind/scripts/cs2/mySection.Rmd`](https://github.com/remindmodel/remind/blob/develop/scripts/cs2/mySection.Rmd) for an example.

## Direct Call and mif-Files

A simple direct call of `compareScenarios2()` may look like this:

```{r}
library(remind2)
compareScenarios2(
  mifScen = c("path/to/Base.mif", "path/to/NDC.mif"),
  mifHist = "path/to/historical.mif",
  outputFile = "CompareScenarios2Example")
```

For further examples and a description of further optional arguments to the function, see `?remind2::compareScenarios2`.

It is possible to use paths to the cluster if called at PIK in the local network (e.g., `/p/tmp/username/...`) or in VPN (e.g., `//clusterfs.pik-potsdam.de/tmp/username/...`).


# Interactive Use of the Rmd-files


In this section, we want to execute individual R-code chunks in the cs2-Rmd-files interactively in RStudio.

First we need access to the Rmd-files. Here we essentially have two options.

## Using outputFormat = "Rmd"

We call `remind2::compareScenarios2()` with `outputFormat = "Rmd"` to obtain a (modified) copy of the Rmd-files.

```{r}
library(remind2)
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif", "path/to/scen3.mif"), # TODO.
  mifHist = "path/to/historical.mif", # TODO.
  outputDir = "path/to/where/rmds/should/be/copied/to", # TODO.
  outputFormat = "Rmd",
  # Add current time as output name to not overwrite other things:
  outputFile = format(Sys.time(), "CompScen2-%Y%m%d-%H%M%S"))
```

The code in these Rmd-files is structured in chunks and each chunk can be run separately by clicking on its play-button. We first open `cs2_main.Rmd`. At the end of the file, there is a chunk
````
```{r prepare mark}
# CLICK "RUN ALL CHUNKS ABOVE" HERE TO PREPARE THE ENVIRONMENT
```
```` 
Clicking on the *triangle above bar*-button on the right executes all chunks above and by that loads and prepares the data for plotting. After that we can open any section-Rmd-file and execute a chunk to create the respective plots. The plots should appear in RStudio inside the Rmd-file below the chunk.

## Using a cloned remind2 repository

Clone the [remind2 repository](https://github.com/pik-piam/remind2). Open a section-Rmd-file `cs2_NN_XXXX.Rmd` in RStudio. 

Now we want to load the `data` object so that the code-chunks can be executed. If we have VPN or are in the local network at PIK, we can load the data from the latest automated model tests (AMT) via `remind2::loadModeltest()`. If this is not possible or we want other mifs to be loaded, we can use `remind2::loadCs2Data()` to create the `data` object. See the help pages (`?<funName>`) of these functions for more information. Now the chunks in the Rmd-files should be executable.



# Workflow for Adding a New Plot to CompareScenarios2

1. If not done already, fork <https://github.com/pik-piam/remind2>.
2. In your personal github remind2 repository, create a new branch.
3. Clone the repository and switch to the newly created branch to get your local copy.
4. In your local copy, open `remind2.Rproj` in RStudio.
5. Press `CTRL+SHIFT+L` to call `devtools::load_all(".")`, which loads `remind2` from your local copy.
6. If it is sufficient to test your new plots on the latest AMTs and you are connected to the PIK network (possibly via VPN), call `loadModeltest()`. Otherwise call an adapted form of 

```{r}
loadCs2Data(
  c("path/to/scen1.mif", "path/to/scen2.mif"), # TODO.
  "path/to/historical.mif") # TODO.
```

This might take some time (up to 1min). After this, an R-object `data` should be available. Test this by typing `data` into the RStudio Console. The first rows of a *tibble* containing some REMIND data should appear. If a bunch of R-code appears, something went wrong.

7. Open the section-Rmd-file in which you want to add the plot. The files are in the folder `inst/markdown/compareScenarios2/` and have names of the form `cs2_NN_XXXX.Rmd`, where `NN` is a two digit number and `XXXX` resembles the section title.
8. You should be able to execute any chunk in the section Rmd by clicking the play button in its top right corner.
9. Insert a new chunk by copying an old one or by pressing `CTRL+ALT+I`. Note: It is better to not assign names to the chunks as cs2 will crash if you used the same name twice.
10. Add a new plot inside the chunk, e.g., `showLinePlots(data, "Your|Variable|Name")`. See [Plot Functions] below.
11. Run your newly created chunk to see the plot.
12. Run the following code to see your new plot in a PDF.

```{r}
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif"), # TODO.
  mifHist = "path/to/historical.mif", # TODO.
  outputFile = format(Sys.time(), "cs2-%Y%m%d-%H%M%S"),
  sections = NN) # TODO: Replace NN by the number of the section you changed 
# (or by "all" to build the whole compare scenarios file, which will take a while).
```

13. Commit your changes. In the commit message, you may use the shorthand `cs2` to indicate that you made a change to compareScenarios2, e.g., `cs2: added plot of My|Variable`.
14. Make sure you pulled all recent changes to remind2. Then, call `lucode2::buildLibrary()` to check the code and increase the version number of the package. Commit again with the commit message `` `lucode2::buildLibrary()` ``. Push your commits to github.
15. Create a pull request of your branch to the `master` branch of the `pik-piam/remind2` repository.

# cs2_main.Rmd

This file loads the data from the mif-files, preprocesses the data, and includes the section-Rmd-files at the very end (and optionally further Rmd-files provided by the user, see YAML-parameter `userSectionPath`).

## YAML-header

The file `cs2_main.Rmd` starts with a YAML header marked by `---`. This header declares some basic information of the report, like its title and the output format. Furthermore, it contains a list `params`, which parameterizes the report. Among others, such parameters are the paths to the mif-files and certain properties that are shared for all plots in the report. Each such parameter can be changed by a respective argument in the call of `compareScenarios2()`, see section *YAML Parameters* in the documentation of the function.

## Loading

The mif-files are loaded using `quitte::read.quitte()`. This function names the global region `"World"` (not `"GLO"` as `magclass::read.report()`). For each file, we obtain one data-frame with columns `model, scenario, region, variable, unit, period, value`. During preprocessing the data-frames are concatenated into one quitte object named `data`. In the sections, `data` is used to provide the data necessary for the plots.

If provided, also config files are loaded.

## Preprocessing

* Scenarios are renamed if the user specifies new names (using a named vector for the argument `mifScen` of `compareScenarios2()` or by setting the parameter `mifScenNames` in the Rmd-files) or if scenario names are duplicate.
* The columns `period` (years) and `region` are filtered according to the parameters `yearsScen`, `yearsHist`, and `reg`.
* `|+|, |++|, |+++|, ...` are removed from variable names. See also `remind2::deletePlus`. An additional column `varplus` is added to the data frame, which retains the original name including `+`. This column is used by `mip::showAreaAndBarPlotsPlus()`.
* For a specified list of variables, a new per-capita-variable is created with the name `"<OLD_NAME> pCap"`.
* For a specified list of variables, a new per-GDP-variable is created with the name `"<OLD_NAME> pGDP"`. As the denominator, the value of `GDP|PPP pCap` is used.

## Global Variables 

Global variables are created in `cs2_main.Rmd` and are intended to be used in the plot functions of the section-Rmd-files.

The quitte-object (data frame) `data` with columns `model, scenario, region, variable, unit, period, value, varplus` provides all data that may be plotted.
It has mostly factor-columns. Thus, a vector of all available regions can be obtained by `levels(data$region)`.

Some arguments of the `mip::show...()` plot functions use the functionality provided by the base-R functions `options()` and `getOption()`. In `cs2_main.Rmd` there are calls to `options()`, setting values of the global options `mip.mainReg`, `mip.yearsBarPlot`, and `mip.histRefModel`. The plotting functions may have an argument, e.g., `mainReg` with default value `getOption("mip.mainReg")`. Thus, this argument does not have to be stated for each call of the plot function (assuming the respective call of `options()` sets it to the right value).

# Section-Rmd-files

The section-Rmd-files follow the naming pattern `cs2_NN_XXXX.Rmd`, where `NN` is replaced by a two digit number and `XXXX` is replaced by a short name of the section. If the YAML-parameter `sections` is set to `"all"`, the default, all sections of this naming pattern are included in `cs2_main.Rmd`. Alternatively, `sections` can be set to a vector of individual sections in the form of `"NN_XXXX"` to only render these sections.

The section-Rmd-files consist of section and sub-section titles, marked by `#`, `##`, `###`, ..., and R-code chunks which create plots, usually by calling one of the `show...()`-functions in the `mip` package.

## userSectionPath

The user can provide one or more additional Rmd-files that are appended after the sections provided by the package. Setting `sections` to `NULL` and `userSectionPath` to a character-vector of paths to Rmd-files creates a fully user-defined report.

## Special Sections

There is a first section (section number 0) and a last section in the files `cs2_00_info.Rmd` and `cs2_99_further_info.Rmd`, respectively. 

### 0 Info {-}

This section contains a file reference table with scenario names and the paths to the respective mif files. It also show if a scenario is renamed. Renaming can be forced by the user by using a named character vector as argument `mifScen` where the names indicate the new scenario name, e.g.,

```{r}
compareScenarios2(
  mifScen = c(newName1 = "path/to/scen1.mif", newName2 = "path/to/scen2.mif"),
  ...)
```

Or, if two scenarios have the same name, they are renamed automatically.

Furthermore, this section displays a description of each scenario. This requires the YAML-parameter `cfgScen` to be set (see also [99 Further Info]). The description can be set in the `secenario_config*.csv`-file via a column `description`.


### 99 Further Info {-}

If `compareScenarios2()` is provided with paths to the `config.Rdata` files of the scenarios via the YAML-parameter `cfgScen` and the path to `default.cfg` ([this](https://github.com/remindmodel/remind/tree/develop/config/default.cfg) file) via `cfgDefault` an analysis of the configurations of the scenarios is shown.

```{r}
compareScenarios2(
  mifScen = c("path/to/scen1.mif", "path/to/scen2.mif"),
  cfgScen = c("path/to/scen1/config.RData", "path/to/scen2/config.RData"),
  cfgDefault = "path/to/default.cfg",
  ...)
```


# Content Functions

## Plot Functions

The section Rmd-files mostly consist of simple calls of a `show...()`-function from the the [mip](https://github.com/pik-piam/mip) package. These functions are designed to make the creation of re-occurring kinds of plots in comapreSceanrios2 simple. Alternatively, one can build custom plots using `ggplot2`.

The `mip`-package contains following default plot functions for comapareScenarios2: 

* `showAreaAndBarPlots()`
* `showAreaAndBarPlotsPlus()`
* `showLinePlots()`
* `showLinePlotsWithTarget()`
* `showMultiLinePlots`
* `showMultiLinePlotsByVariable()`
* `showRegiLinePlots()`

All but `showLinePlotsWithTarget()` can use the global option `mip.mainReg`.
`showAreaAndBarPlots()` and `showAreaAndBarPlotsPlus()` can use `mip.yearsBarPlot`.
`showMultiLinePlotsByVariable()` uses `mip.histRefModel`.

See the respective function documentation for more information and example plots.

## Table Functions

For creating tables in cs2, see the documentation of `remind2::calcTimeSeriesStats()` and `remind2::showStatsTable()` and -- for an example -- the section **Tables of Significant Periods** in [`remind2/inst/markdown/compareScenarios2/cs2_01_summary.Rmd`](https://github.com/pik-piam/remind2/blob/master/inst/markdown/compareScenarios2/cs2_01_summary.Rmd).
