# Energy Supply

## Investments Electricity

```{r}
items <- c(
  "Energy Investments|Elec|Biomass|w/ CCS", 
  "Energy Investments|Elec|Biomass|w/o CCS", 
  "Energy Investments|Elec|Coal|w/ CCS", 
  "Energy Investments|Elec|Coal|w/o CCS", 
  "Energy Investments|Elec|Fossil", 
  "Energy Investments|Elec|Gas|w/ CCS", 
  "Energy Investments|Elec|Gas|w/o CCS", 
  "Energy Investments|Elec|Geothermal", 
  "Energy Investments|Elec|Grid", 
  "Energy Investments|Elec|Hydro", 
  "Energy Investments|Elec|Hydrogen", 
  "Energy Investments|Elec|Nuclear", 
  "Energy Investments|Elec|Oil", 
  "Energy Investments|Elec|Solar", 
  "Energy Investments|Elec|Storage", 
  "Energy Investments|Elec|Wind")
showAreaAndBarPlots(data, items)
```

## Capacities Electricity

```{r}
items <- c(
  "Cap|Electricity|Coal|w/ CCS",
  "Cap|Electricity|Coal|w/o CCS",
  "Cap|Electricity|Gas|w/ CCS",
  "Cap|Electricity|Gas|w/o CCS",
  "Cap|Electricity|Oil|w/o CCS",
  "Cap|Electricity|Biomass",
  "Cap|Electricity|Nuclear",
  "Cap|Electricity|Hydro",
  "Cap|Electricity|Geothermal",
  "Cap|Electricity|Hydrogen",
  "Cap|Electricity|Storage|Battery",
  "Cap|Electricity|Solar",
  if ("Cap|Electricity|Wind|Offshore" %in% variables)
    c("Cap|Electricity|Wind|Onshore", "Cap|Electricity|Wind|Offshore")
  else
    "Cap|Electricity|Wind"
  )
showAreaAndBarPlots(data, items)
```

## Capacities electricity line plots

### Nuclear
```{r}
showLinePlots(data, "Cap|Electricity|Nuclear")
```

### Hydro
```{r}
showLinePlots(data, "Cap|Electricity|Hydro")
```

### Wind
```{r}
showLinePlots(data, "Cap|Electricity|Wind")
showLinePlots(data, "Cap|Electricity|Wind|Onshore")
showLinePlots(data, "Cap|Electricity|Wind|Offshore")
```

### Solar
```{r}
showLinePlots(data, "Cap|Electricity|Solar")
```

### Coal
```{r}
showLinePlots(data, "Cap|Electricity|Coal")
```

### Coal
```{r}
showLinePlots(data, "Cap|Electricity|Gas")
```

### Oil
```{r}
showLinePlots(data, "Cap|Electricity|Oil")
```

### Biomass
```{r}
showLinePlots(data, "Cap|Electricity|Biomass")
```

### Hydrogen
```{r}
showLinePlots(data, "Cap|Electricity|Hydrogen")
```

## PE Mix
### PE|Coal
```{r}
items <- c(
  "PE|Coal|Gases",
  "PE|Coal|Liquids",
  "PE|Coal|Solids",
  "PE|Coal|Heat",
  "PE|Coal|Electricity",
  "PE|Coal|Hydrogen")
showAreaAndBarPlots(data, items)
```

### PE|Coal
```{r}
items <- c(
  "PE|Gas|Gases",
  "PE|Gas|Heat",
  "PE|Gas|Electricity|w/ CCS",
  "PE|Gas|Electricity|w/o CCS",
  "PE|Gas|Liquids|w/ CCS",
  "PE|Gas|Liquids|w/o CCS",
  "PE|Gas|Hydrogen|w/ CCS",
  "PE|Gas|Hydrogen|w/o CCS")
showAreaAndBarPlots(data, items)
```


### PE|Biomass

```{r}
items <- c(
  "PE|Biomass|Solids",
  "PE|Biomass|Heat",
  "PE|Biomass|Liquids|w/ CCS",
  "PE|Biomass|Liquids|w/o CCS",
  "PE|Biomass|Gases",
  "PE|Biomass|Electricity|w/ CCS",
  "PE|Biomass|Electricity|w/o CCS",
  "PE|Biomass|Hydrogen|w/ CCS",
  "PE|Biomass|Hydrogen|w/o CCS")
showAreaAndBarPlots(data, items)
```

## Primary Energy line plots

```{r}
showLinePlots(data, "PE|Coal")
showLinePlots(data, "PE|Oil")
showLinePlots(data, "PE|Gas")
showLinePlots(data, "PE|Biomass")
showLinePlots(data, "Primary Energy Production|Biomass|Energy Crops")
```

### PE|Coal|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Coal")
```

### PE|Oil|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Oil")
```

### PE|Gas|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Gas")
```

## Secondary Energy Mixes
### SE|Liquids

```{r}
items <- c(
  "SE|Liquids|Oil",
  "SE|Liquids|Biomass|w/ CCS",
  "SE|Liquids|Biomass|w/o CCS",
  "SE|Liquids|Coal|w/ CCS",
  "SE|Liquids|Coal|w/o CCS",
  "SE|Liquids|Gas|w/ CCS",
  "SE|Liquids|Gas|w/o CCS",
  "SE|Liquids|Hydrogen",
  "SE|Liquids|Hydrogen|Net Imports")
showAreaAndBarPlots(data, items)
```

### SE|Gases
```{r}
items <- c(
  "SE|Gases|Natural Gas",
  "SE|Gases|Biomass|w/ CCS",
  "SE|Gases|Biomass|w/o CCS",
  "SE|Gases|Coal|w/ CCS",
  "SE|Gases|Coal|w/o CCS",
  "SE|Gases|Hydrogen")
showAreaAndBarPlots(data, items)
```

### SE|Hydrogen
```{r}
items <- c(
  "SE|Hydrogen|Biomass|w/ CCS",
  "SE|Hydrogen|Biomass|w/o CCS",
  "SE|Hydrogen|Coal|w/ CCS",
  "SE|Hydrogen|Coal|w/o CCS",
  "SE|Hydrogen|Gas|w/ CCS",
  "SE|Hydrogen|Gas|w/o CCS",
  "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
  "SE|Hydrogen|Electricity|Standard Electrolysis",
  "SE|Hydrogen|Net Imports")
showAreaAndBarPlots(data, items)
```

### SE|Hydrogen - Usage
```{r}
items <- c(
  "FE|Industry|Hydrogen",
  "FE|Buildings|Hydrogen",
  "FE|Transport|Hydrogen",
  "FE|CDR|Hydrogen",
  "SE|Hydrogen|used for electricity|normal turbines",
  "SE|Hydrogen|used for electricity|forced VRE turbines",
  "SE|Hydrogen|used for synthetic fuels|liquids",
  "SE|Hydrogen|used for synthetic fuels|gases")
showAreaAndBarPlots(data, items)
```

### SE|Electricity - Usage
```{r}
items <- c(
  "SE|Electricity|used for H2|for synthetic fuels|gases",
  "SE|Electricity|used for H2|for synthetic fuels|liquids",
  "SE|Electricity|used for H2|direct FE H2",
  "SE|Electricity|used for H2|VRE Storage",
  "SE|Electricity|used in Buildings",
  "SE|Electricity|used in Industry",
  "SE|Electricity|used in Transport",
  "SE|Electricity|used for CDR",
  "SE|Electricity|used for own consumption of energy system")
showAreaAndBarPlots(data, items)
```

### SE|Solids
```{r}
items <- c(
  "SE|Solids|Biomass",
  "SE|Solids|Traditional Biomass",
  "SE|Solids|Coal")
showAreaAndBarPlots(data, items)
```

### SE|Heat
```{r}
items <- c(
  "SE|Heat|Biomass",
  "SE|Heat|Coal",
  "SE|Heat|Gas",
  "SE|Heat|Electricity|Heat Pumps")
showAreaAndBarPlots(data, items)
```

## Secondary Energy line plots
### SE|Gases
```{r}
showLinePlots(data,  c("SE|Gases|Natural Gas", "SE|Gases|Gas"))
showLinePlots(data, "SE|Gases|Coal")
showLinePlots(data, "SE|Gases|Biomass")
```

### SE|Electricity
```{r}
showLinePlots(data, "SE|Electricity|Gas")
showLinePlots(data, "SE|Electricity|Coal")
showLinePlots(data, "SE|Electricity|Oil")
showLinePlots(data, "SE|Electricity|Hydro")
showLinePlots(data, "SE|Electricity|Wind")
showLinePlots(data, "SE|Electricity|Nuclear")
showLinePlots(data, "SE|Electricity|Solar")
showLinePlots(data, "SE|Electricity|Biomass")
```

### SE|Solids
```{r}
showLinePlots(data, "SE|Solids|Coal")
showLinePlots(data, "SE|Solids|Biomass")
showLinePlots(data, "SE|Solids|Traditional Biomass")
```
