# Energy Demand

## Final Energy total

### Basics

```{r}
tot <- "FE"
items <- c(
  "FE|Electricity",
  "FE|Gases",
  "FE|Heat",
  "FE|Solids",
  "FE|Liquids",
  "FE|Hydrogen")
```

\newpage

#### FE|* Area Plots

```{r}
showAreaAndBarPlots(data, items, tot)
showAreaAndBarPlots(data, items, tot, fill = TRUE)
```

#### FE|* Line Plots

```{r}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### FE|Electricity|Share

```{r}
showLinePlots(data, "FE|Electricity|Share")
```

## Buildings Final Energy

### Basics

```{r}
tot <- "FE|Buildings"
items <- c(
  "FE|Buildings|Electricity",
  "FE|Buildings|Gases",
  "FE|Buildings|Heat",
  "FE|Buildings|Solids",
  "FE|Buildings|Liquids",
  "FE|Buildings|Hydrogen")
```

\newpage

#### FE|Buildings|* Area Plots

```{r}
showAreaAndBarPlots(data, items, tot)
showAreaAndBarPlots(data, items, tot, fill = TRUE)
```

#### FE|Buildings|* Line Plots

```{r}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### FE|Buildings|Electricity|Share

```{r}
showLinePlots(data, "FE|Buildings|Electricity|Share")
```


## Industry Final Energy

### Basics

```{r}
tot <- "FE|Industry"
items <- c(
  "FE|Industry|Electricity",
  "FE|Industry|Gases",
  "FE|Industry|Heat",
  "FE|Industry|Solids",
  "FE|Industry|Liquids",
  "FE|Industry|Hydrogen")
```

\newpage

#### FE|Industry|* Area Plots

```{r}
showAreaAndBarPlots(data, items, tot)
showAreaAndBarPlots(data, items, tot, fill = TRUE)
```

#### FE|Industry|* Line Plots

```{r}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### FE|Industry|Electricity|Share

```{r}
showLinePlots(data, "FE|Industry|Electricity|Share")
```


### FE mix Steel
```{r}
tot <- "FE|Industry|Steel"
items <- c(
  "FE|Industry|Steel|Heat",
  "FE|Industry|Steel|Hydrogen",
  "FE|Industry|Steel|Solids",
  "FE|Industry|Steel|Liquids",
  "FE|Industry|Steel|Gases",
  "FE|Industry|Steel|Primary|Electricity",
  "FE|Industry|Steel|Secondary|Electricity")
showAreaAndBarPlots(data, items, tot)
```

### FE mix Cement
```{r}
tot <- "FE|Industry|Cement"
items <- c(
  "FE|Industry|Cement|Heat",
  "FE|Industry|Cement|Hydrogen",
  "FE|Industry|Cement|Solids",
  "FE|Industry|Cement|Liquids",
  "FE|Industry|Cement|Gases",
  "FE|Industry|Cement|Electricity")
showAreaAndBarPlots(data, items, tot)
```

### FE mix Non-metallic minerals
```{r}
tot <- "FE|Industry|Non-metallic minerals"
items <- c(
  "FE|Industry|Electricity|Non-metallic minerals",
  "FE|Industry|Gases|Non-metallic minerals",
  "FE|Industry|Heat|Non-metallic minerals",
  "FE|Industry|Hydrogen|Non-metallic minerals",
  "FE|Industry|Liquids|Non-metallic minerals",
  "FE|Industry|Solids|Non-metallic minerals")
showAreaAndBarPlots(data, items, tot)
```

### FE mix Chemicals
```{r}
tot <- "FE|Industry|Chemicals"
items <- c(
  "FE|Industry|Chemicals|Heat",
  "FE|Industry|Chemicals|Hydrogen",
  "FE|Industry|Chemicals|Solids",
  "FE|Industry|Chemicals|Liquids",
  "FE|Industry|Chemicals|Gases",
  "FE|Industry|Chemicals|Electricity|Mechanical work and low-temperature heat",
  "FE|Industry|Chemicals|Electricity|High-temperature heat")
showAreaAndBarPlots(data, items, tot)
```

### FE mix Other Industry
```{r}
tot <- "FE|Industry|Other Industry"
items <- c(
  "FE|Industry|Other Industry|Heat",
  "FE|Industry|Other Industry|Hydrogen",
  "FE|Industry|Other Industry|Solids",
  "FE|Industry|Other Industry|Liquids",
  "FE|Industry|Other Industry|Gases",
  "FE|Industry|Other Industry|Electricity|Mechanical work and low-temperature heat",
  "FE|Industry|Other Industry|Electricity|High-temperature heat")
showAreaAndBarPlots(data, items, tot)
```

### FE|Industry|* line plots
```{r}
showLinePlots(data, "FE|Industry|Steel")
showLinePlots(data, "FE|Industry|Steel|Primary")
showLinePlots(data, "FE|Industry|Steel|Secondary")
showLinePlots(data, "FE|Industry|Cement")
showLinePlots(data, "FE|Industry|Non-metallic minerals")
showLinePlots(data, "FE|Industry|Chemicals")
showLinePlots(data, c("FE|Industry|Other Industry", "FE|Industry|other"))
```


### FE|Non-energy Use|Industry per carrier and SE origin

```{r}
tot <- "FE|Non-energy Use|Industry"
items <- c(
  "FE|Non-energy Use|Industry|Solids|Fossil",
  "FE|Non-energy Use|Industry|Solids|Biomass",
  "FE|Non-energy Use|Industry|Liquids|Fossil",
  "FE|Non-energy Use|Industry|Liquids|Biomass",
  "FE|Non-energy Use|Industry|Liquids|Hydrogen",
  "FE|Non-energy Use|Industry|Gases|Fossil",
  "FE|Non-energy Use|Industry|Gases|Biomass",
  "FE|Non-energy Use|Industry|Gases|Hydrogen")
showAreaAndBarPlots(data, items, tot)
```



### Specific Energy Consumption

```{r}
items <- c(
  "FE|Industry|Specific Energy Consumption|Chemicals",
  "FE|Industry|Specific Energy Consumption|Other Industry")
walk(items, showLinePlots, data = data)
```

### Specific Energy Consumption with thermodynamic limits
```{r}
# estimated values for thermodynamic limits are hardcoded here. Could be improved

# Cement and other non-metallic minerals
var1 <- "FE|Industry|Specific Energy Consumption|Cement"
data %>%
  filter(variable == var1) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for cement",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var1,
      value = 1.8)) %>% # GJ/t. # nolint
  showLinePlots(var1)

# Primary steel
var2 <- "FE|Industry|Specific Energy Consumption|Primary Steel"
data %>%
  filter(variable == var2) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for primary steel",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var2,
      value = 8.2)) %>% # GJ/t. # nolint
  showLinePlots(var2)

# Secondary steel
var3 <- "FE|Industry|Specific Energy Consumption|Secondary Steel"
data %>%
  filter(variable == var3) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for secondary steel",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var3,
      value = 1.3)) %>% # GJ/t. # nolint
  showLinePlots(var3)
```


## Transport Final Energy 

### Basics -- with Bunkers

```{r}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Gases",
  "FE|Transport|Liquids",
  "FE|Transport|Hydrogen")
items2 <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Gases",
  "FE|Transport|Liquids|Biomass",
  "FE|Transport|Liquids|Fossil",
  "FE|Transport|Liquids|Hydrogen",
  "FE|Transport|Hydrogen")
```

\newpage

#### FE|Transport|* Area Plots -- with Bunkers

```{r}
showAreaAndBarPlots(data, items, tot)
showAreaAndBarPlots(data, items2, tot)
showAreaAndBarPlots(data, items, tot, fill = TRUE)
```

#### FE|Transport|* Line Plots -- with Bunkers

```{r}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### FE|Transport|Electricity|Share

```{r}
showLinePlots(data, "FE|Transport|Electricity|Share")
```


### Basics -- w/o Bunkers

```{r}
tot <- "FE|Transport|w/o Bunkers"
items <- c(
  "FE|Transport|w/o Bunkers|Electricity",
  "FE|Transport|w/o Bunkers|Gases",
  "FE|Transport|w/o Bunkers|Liquids",
  "FE|Transport|w/o Bunkers|Hydrogen")
items2 <- c(
  "FE|Transport|w/o Bunkers|Electricity",
  "FE|Transport|w/o Bunkers|Gases",
  "FE|Transport|w/o Bunkers|Liquids|Biomass",
  "FE|Transport|w/o Bunkers|Liquids|Fossil",
  "FE|Transport|w/o Bunkers|Liquids|Hydrogen",
  "FE|Transport|w/o Bunkers|Hydrogen")
```

\newpage

#### FE|Transport|* Area Plots -- w/o Bunkers

```{r}
showAreaAndBarPlots(data, items, tot)
showAreaAndBarPlots(data, items2, tot)
showAreaAndBarPlots(data, items, tot, fill = TRUE)
```

#### FE|Transport|* Line Plots -- w/o Bunkers

```{r}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```


### Transport per type

```{r}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|LDV|Liquids",
  "FE|Transport|LDV|Gases",
  "FE|Transport|LDV|Electricity",
  "FE|Transport|LDV|Hydrogen",
  "FE|Transport|non-LDV|Liquids",
  "FE|Transport|non-LDV|Gases",
  "FE|Transport|non-LDV|Electricity",
  "FE|Transport|non-LDV|Hydrogen")
showAreaAndBarPlots(data, items, tot)
```

### Bunkers

```{r}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|Bunkers",
  "FE|Transport|w/o Bunkers")
showAreaAndBarPlots(data, items, tot)
```
