# Energy Services and Products

## FE|Buildings
```{r}
tot <- "FE|Buildings"
items <- c(
  "FE|Buildings|non-Heating|Electricity|Conventional",
  "FE|Buildings|Heating|Electricity|Resistance",
  "FE|Buildings|Heating|Electricity|Heat pumps",
  "FE|Buildings|Heating|District Heating",
  "FE|Buildings|Heating|Solids",
  "FE|Buildings|Heating|Liquids",
  "FE|Buildings|Heating|Gases",
  "FE|Buildings|Heating|Hydrogen")
showAreaAndBarPlots(data, items, tot)
```

### Region Intercomparison FE|Buildings

```{r}
items <- c(
  "FE|Buildings|Heating",
  "FE|Buildings|Appliances and Light",
  "FE|Buildings|Cooking and Water",
  "FE|Buildings|Space Cooling",
  "FE|Buildings|Space Heating")
showMultiLinePlots(data, items[1:3])
showMultiLinePlots(data, items[4:5])
showMultiLinePlotsByVariable(data, items[1:3], "GDP|PPP pCap")
showMultiLinePlotsByVariable(data, items[4:5], "GDP|PPP pCap")
```


## Transport
### Energy Services for Passenger Transport
```{r}
items <- c(
  "ES|Transport|Pass pCap",
  "ES|Transport|Pass|Road|LDV pCap",
  "ES|Transport|Pass|non-LDV pCap")
showMultiLinePlots(data, items)    
showMultiLinePlotsByVariable(data, items, "GDP|PPP pCap")
```

```{r}
##---- ES passenger transport per capita (bar graph)----
items <- c(
  "ES|Transport|Pass|Road|LDV|BEV pCap",
  "ES|Transport|Pass|Road|LDV|FCEV pCap",
  "ES|Transport|Pass|Road|LDV|Gases pCap",
  "ES|Transport|Pass|Road|LDV|Hybrid Electric pCap",
  "ES|Transport|Pass|Road|LDV|Liquids pCap")
showAreaAndBarPlots(data, items)    
```

### Energy Services for Freight Transport per Capita
```{r}
items <- c(
  "ES|Transport|Freight pCap")
showMultiLinePlots(data, items)    
showMultiLinePlotsByVariable(data, items, "GDP|PPP pCap")
```


```{r}
items <- c(
  "ES|Transport|Freight|Road|Electric pCap",
  "ES|Transport|Freight|Road|FCEV pCap",
  "ES|Transport|Freight|Road|Gases pCap",
  "ES|Transport|Freight|Road|Liquids pCap")
showAreaAndBarPlots(data, items)
```

### LDV Vehicles Stock
```{r}
tot <- "Est LDV Stock"
items <- c(
  "Est EV LDV Stock",
  "Est H2 LDV Stock",
  "Est ICE LDV Stock")
showAreaAndBarPlots(data, items, tot)
```

### LDV Vehicles Sales
```{r}
tot <- "Est LDV Sales"
items <- c(
  "Est EV LDV Sales",
  "Est H2 LDV Sales",
  "Est ICE LDV Sales")
showAreaAndBarPlots(data, items, tot)
```

### non-LDV Vehicles Stock
```{r}
tot <- "Services and Products|Transport|non-LDV|Stock|uedit"
items <- c(
  "Services and Products|Transport|non-LDV|Stock|apCarDiT",
  "Services and Products|Transport|non-LDV|Stock|apcarDiEffT",
  "Services and Products|Transport|non-LDV|Stock|apcarDiEffH2T")
showAreaAndBarPlots(data, items, tot)
```

### non-LDV Vehicles Sales
```{r}
tot <- "Services and Products|Transport|non-LDV|Sales|uedit"
items <- c(
  "Services and Products|Transport|non-LDV|Sales|apCarDiT",
  "Services and Products|Transport|non-LDV|Sales|apcarDiEffT",
  "Services and Products|Transport|non-LDV|Sales|apcarDiEffH2T")
showAreaAndBarPlots(data, items, tot) 
```

## Industry Production
### Subsector Production
```{r plot industry subsector production}
showLinePlots(data, "Production|Industry|Cement")
showLinePlots(data, "Value Added|Industry|Chemicals")
showLinePlots(data, "Production|Industry|Steel")
showLinePlots(data, "Production|Industry|Steel|Primary") 
showLinePlots(data, "Production|Industry|Steel|Secondary")
showLinePlots(data, "Value Added|Industry|Other Industry")
```

### Steel Produciton Mix
```{r plot steel production mix, results = 'asis'}
items <- c('Production|Industry|Steel|Primary',
           'Production|Industry|Steel|Secondary')

d_plot <- data %>% 
  filter(variable %in% items) %>% 
  mutate(foo = shorten_legend(variable)) %>% 
  order.levels(foo = rev(shorten_legend(items)))

# Show at max 5 scenario rows by 7 region column plots
for (regions in bin_distribute(getRegs(d_plot), 7)) {
  for (scenarios in bin_distribute(getScenarios(d_plot), 5)) {
    suppressWarnings(
      p <- ggplot_bar_remind_vts(
        data = d_plot %>% 
          filter(scenario %in% scenarios,
                 region %in% regions),
        mapping = aes(x = period, y = value, fill = foo),
        gaps = 0) +
        scale_fill_discrete(breaks = shorten_legend(items),
                            name = attr(shorten_legend(items), 'front')) +
        # fix y-axis across regions (columns)
        geom_blank(
          data = d_plot %>% 
          filter(scenario %in% scenarios,
                 region %in% regions) %>% 
            group_by(region, period, scenario) %>% 
            summarise(value = sum(value), .groups = 'drop_last') %>% 
            mutate(value = max(value)) %>% 
            add_remind_timesteps_columns(),
          mapping = aes(x = xpos, y = value)) +
        facet_wrap(~ interaction(region, scenario, sep = ' '), 
                   nrow = length(scenarios), scales = 'free_y') +
        labs(x = NULL, y = d_plot %>% pull(unit) %>% unique()) +
        theme_minimal() + 
        theme(legend.position = 'bottom')
    )
    plot(p)
    cat('\n\n')
  }
}
```

### Subsector per-Capita Production 
```{r plot subsector per-capita production}
items <- c('Production|Industry|Cement|per-capita',
           'Value Added|Industry|Chemicals|per-capita',
           'Production|Industry|Steel|per-capita',
           'Production|Industry|Steel|Primary|per-capita',
           'Production|Industry|Steel|Secondary|per-capita',
           'Value Added|Industry|Other Industry|per-capita')
walk(items, showLinePlots, data = data, scales = 'fixed')
```


### Steel accumulation
```{r}
stock_t0 <- filter(data, period == 2005, model == "Mueller", variable == "Steel stock") %>% select("region", "value")

population <- filter(data, period >= 2005, model == "REMIND", variable == "Population") %>%
  interpolate_missing_periods(seq(2005, 2100, 1)) %>%
  select("period", "region", "value", "scenario")

years <- c(seq(2005, 2060, 5), seq(2070, 2100, 10)) 

stock <- data %>%
  filter(variable %in% c("Production|Industry|Steel|Primary"), model == "REMIND", period >= 2005) %>%
  interpolate_missing_periods(seq(2005, 2100, 1)) %>%
  group_by(model, region, scenario, variable, unit) %>%
  filter(!is.na(value)) %>%
  arrange(period) %>%
  mutate(cumsum.value = cumsum(value)) %>%
  mutate(variable = "Production|Industry|Steel|Accumulated Production", unit = "million t") %>% 
  ungroup() %>%
  left_join(stock_t0, by = c("region")) %>%
  mutate(value = cumsum.value + value.y) %>%
  select("model", "scenario", "region", "variable", "unit", "period", "value") %>%
  filter(!is.na(value)) %>% 
  filter(period %in% years)

showLinePlots(stock, "Production|Industry|Steel|Accumulated Production", mainReg = "World")

stock_pc <- left_join(stock, population, by = c("period", "region", "scenario")) %>%
  mutate(value = value.x / value.y, unit = "t per cap")

showLinePlots(stock_pc, "Production|Industry|Steel|Accumulated Production", scales = "fixed", mainReg = "World")
```

### Subsector per-GDP Production
```{r plot subsector per-GDP production}
items <- c('Production|Industry|Cement|per-GDP',
           'Value Added|Industry|Chemicals|per-GDP',
           'Production|Industry|Steel|per-GDP',
           'Production|Industry|Steel|Primary|per-GDP',
           'Production|Industry|Steel|Secondary|per-GDP',
           'Value Added|Industry|Other Industry|per-GDP')
walk(items, showLinePlots, data = data, scales = 'fixed')
```

### Subsector per-capita Production over per-capita GDP
```{r plot subsectpr per-capita production over per-capita GDP, results = 'asis'}
items <- c('Production|Industry|Cement|per-capita',
           'Value Added|Industry|Chemicals|per-capita',
           'Production|Industry|Steel|per-capita',
           'Production|Industry|Steel|Primary|per-capita',
           'Production|Industry|Steel|Secondary|per-capita',
           'Value Added|Industry|Other Industry|per-capita')

d_plot <- full_join(
  data %>% 
    select(scenario, region, variable, unit, period, value) %>% 
    filter(variable %in% items),
  
  data %>% 
    filter('GDP|per capita|PPP' == variable) %>% 
    select(scenario, region, period, GDP_pC = value),
  
  c('scenario', 'region', 'period')
)

x_lab <- data %>% 
  filter('GDP|per capita|PPP' == variable) %>% 
  distinct(variable, unit) %>% 
    mutate(label = paste0(variable, ' [', unit, ']')) %>% 
    pull(label)

x_lim <- data %>% 
  filter('GDP|per capita|PPP' == variable) %>% 
  pull(value) %>% 
  range()

for (i in items) {
  cat('\n\n####', sub('.*Industry\\|(.*)\\|per-capita', '\\1', i), '\n')
  
  y_lab <- d_plot %>% 
    filter(i == variable) %>% 
    distinct(variable, unit) %>% 
    mutate(label = paste0(variable, ' [', unit, ']')) %>% 
    pull(label)
    
  p <- ggplot(mapping = aes(x = GDP_pC, y = value, colour = scenario)) +
    geom_line(data = d_plot %>% 
                filter(i == variable,
                       getOption("mip.mainReg") == region) %>% 
                select(-region),
              mapping = aes(linetype = 'World')) +
    scale_linetype_manual(values = c('World' = 'dotted'), name = NULL) +
    geom_line(data = d_plot %>% 
                filter(i == variable,
                       getOption("mip.mainReg") != region)) +
    scale_colour_discrete(name = NULL) +
    facet_wrap(~ region, scales = 'fixed') +
    expand_limits(x = 0, y = 0) +
    labs(x = x_lab, y = y_lab) +
    theme_minimal()
  plot(p)
}
```
