# Energy Demand

## Final Energy total

### Basics

```{r Final Energy total}
tot <- "FE"
items <- c(
  "FE|Electricity",
  "FE|Hydrogen",  
  "FE|Heat",
  "FE|Gases",
  "FE|Liquids",
  "FE|Solids",
  NULL
)
```

\newpage

#### FE Area Plots

```{r FE Area Plots}
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
showAreaAndBarPlots(data, items, tot, orderVars = "user", fill = TRUE)
```

#### FE Line Plots

```{r FE Line Plots}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### FE Electricity Share

```{r FE Electricity Share}
showLinePlots(data, "FE|Electricity|Share")
```

## Buildings Final Energy

### Basics

```{r Buildings Final Energy}
tot <- "FE|Buildings"
items <- c(
  "FE|Buildings|Electricity",
  "FE|Buildings|Hydrogen",
  "FE|Buildings|Heat",  
  "FE|Buildings|Gases",
  "FE|Buildings|Liquids",
  "FE|Buildings|Solids",  
  NULL
)

items2 <- c(
  "FE|Buildings|Electricity",
  "FE|Buildings|Hydrogen",
  "FE|Buildings|Heat",
  "FE|Buildings|Gases|Hydrogen",
  "FE|Buildings|Gases|Biomass",  
  "FE|Buildings|Gases|Fossil",
  "FE|Buildings|Liquids|Hydrogen",    
  "FE|Buildings|Liquids|Biomass",
  "FE|Buildings|Liquids|Fossil",
  "FE|Buildings|Solids|Biomass",
  "FE|Buildings|Solids|Fossil",
  NULL
)
```

\newpage

#### FE Buildings Area Plots

```{r FE Buildings Area Plots}
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
showAreaAndBarPlots(data, items, tot, orderVars = "user", fill = TRUE)
showAreaAndBarPlots(data, items2, tot, orderVars = "user", scales = "fixed")
```

#### FE Buildings Line Plots

```{r FE Buildings Line Plots}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### Electricity Share in Buildings Final Energy

```{r Electricity Share in Buildings Final Energy}
showLinePlots(data, "FE|Buildings|Electricity|Share")
```


## Industry Final Energy

### Basics

```{r Industry Final Energy}
tot <- "FE|Industry"
items <- c(
  "FE|Industry|Electricity",
  "FE|Industry|Hydrogen",
  "FE|Industry|Heat",  
  "FE|Industry|Gases",
  "FE|Industry|Liquids",
  "FE|Industry|Solids",  
  NULL)

items2 <- c(
  "FE|Industry|Electricity",
  "FE|Industry|Hydrogen",
  "FE|Industry|Heat",
  "FE|Industry|Gases|Hydrogen",
  "FE|Industry|Gases|Biomass",  
  "FE|Industry|Gases|Fossil",
  "FE|Industry|Liquids|Hydrogen",    
  "FE|Industry|Liquids|Biomass",
  "FE|Industry|Liquids|Fossil",
  "FE|Industry|Solids|Biomass",
  "FE|Industry|Solids|Fossil",
  NULL)

```

\newpage

#### FE Industry Area Plots

```{r FE Industry Area Plots}
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
showAreaAndBarPlots(data, items, tot, orderVars = "user", fill = TRUE)
showAreaAndBarPlots(data, items2, tot, orderVars = "user", scales = "fixed")
```

#### FE Industry Line Plots

```{r FE Industry Line Plots}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### Electricity Share in Industry Final Energy

```{r Electricity Share in Industry Final Energy}
showLinePlots(data, "FE|Industry|Electricity|Share")
```

### FE mix Steel
```{r FE mix Steel}
tot <- "FE|Industry|Steel"
items <- c(
  "FE|Industry|Steel|Secondary|Electricity",
  "FE|Industry|Steel|Primary|Electricity",  
  "FE|Industry|Steel|Hydrogen",  
  "FE|Industry|Steel|Gases",  
  "FE|Industry|Steel|Liquids",  
  "FE|Industry|Steel|Solids",  
  NULL)
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```

### FE mix Steel using process-based steel modeling by route
```{r FE mix Steel route}
if ("FE|Industry|Steel|BF-BOF" %in% levels(data$variable)){ # if process-based steel is used
  tot <- "FE|Industry|Steel"
  items <- c(
    "FE|Industry|Steel|DRI-NG-EAF-CCS",
    "FE|Industry|Steel|DRI-NG-EAF",
    "FE|Industry|Steel|DRI-H2-EAF",
    "FE|Industry|Steel|BF-BOF-CCS",
    "FE|Industry|Steel|BF-BOF",
    "FE|Industry|Steel|SCRAP-EAF")
  # Non-process based scenarios have tot variable, but not items, which leads to errors in display;
  # Therefore, filter data by scenarios that have the 'items' variables.
  dscens <- data %>%
    filter(.data$variable %in% items, .data$scenario != "historical") %>%
    droplevels() %>%
    pull('scenario') %>%
    unique()
  droute <- data %>%
    filter(.data$scenario %in% dscens)
showAreaAndBarPlots(droute, items, tot, orderVars="user", scales = "fixed")
}
```

### FE mix Cement
```{r FE mix Cement}
tot <- "FE|Industry|Cement"
items <- c(
  "FE|Industry|Cement|Electricity",
  "FE|Industry|Cement|Hydrogen",  
  "FE|Industry|Cement|Gases",
  "FE|Industry|Cement|Liquids",
  "FE|Industry|Cement|Solids",
  NULL
)
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```

### FE mix Non-metallic minerals
```{r FE mix Non-metallic minerals}
tot <- "FE|Industry|Non-metallic minerals"
items <- c(
  "FE|Industry|Electricity|Non-metallic minerals",
  "FE|Industry|Hydrogen|Non-metallic minerals",  
  "FE|Industry|Heat|Non-metallic minerals",  
  "FE|Industry|Gases|Non-metallic minerals",
  "FE|Industry|Liquids|Non-metallic minerals",
  "FE|Industry|Solids|Non-metallic minerals")
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```

### FE mix Chemicals
```{r FE mix Chemicals}
tot <- "FE|Industry|Chemicals"
items <- c(
  "FE|Industry|Chemicals|Electricity|Mechanical work and low-temperature heat",
  "FE|Industry|Chemicals|Electricity|High-temperature heat",
  "FE|Industry|Chemicals|Hydrogen",  
  "FE|Industry|Chemicals|Gases",
  "FE|Industry|Chemicals|Solids",
  "FE|Industry|Chemicals|Liquids",
  NULL)
showAreaAndBarPlots(data, items, tot, scales = "fixed")
```

### FE Total Chemicals
```{r FE Total Chemicals}
items <- c(
  "FE|Industry|Chemicals") 
showLinePlots(data, items)
```

### FE mix Other Industry
```{r FE mix Other Industry}
tot <- "FE|Industry|Other Industry"
items <- c(
  "FE|Industry|Other Industry|Electricity|Mechanical work and low-temperature heat",
  "FE|Industry|Other Industry|Electricity|High-temperature heat",
  "FE|Industry|Other Industry|Hydrogen",
  "FE|Industry|Other Industry|Heat",  
  "FE|Industry|Other Industry|Gases",
  "FE|Industry|Other Industry|Liquids",  
  "FE|Industry|Other Industry|Solids",
  NULL)
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```

### FE Industry line plots
```{r FE Industry line plots}
showLinePlots(data, "FE|Industry|Steel")
showLinePlots(data, "FE|Industry|Steel|Primary")
showLinePlots(data, "FE|Industry|Steel|Secondary")
showLinePlots(data, "FE|Industry|Cement")
showLinePlots(data, "FE|Industry|Non-metallic minerals")
showLinePlots(data, "FE|Industry|Chemicals")
showLinePlots(data, c("FE|Industry|Other Industry", "FE|Industry|other"))
```


### FE Non-energy Use Industry per carrier and SE origin

```{r FE Non-energy Use Industry per carrier and SE origin}
tot <- "FE|Non-energy Use|Industry"
items <- c(
  "FE|Non-energy Use|Industry|Solids|Fossil",
  "FE|Non-energy Use|Industry|Solids|Biomass",
  "FE|Non-energy Use|Industry|Liquids|Fossil",
  "FE|Non-energy Use|Industry|Liquids|Biomass",
  "FE|Non-energy Use|Industry|Liquids|Hydrogen",
  "FE|Non-energy Use|Industry|Gases|Fossil",
  "FE|Non-energy Use|Industry|Gases|Biomass",
  "FE|Non-energy Use|Industry|Gases|Hydrogen")
showAreaAndBarPlots(data, items, tot)
```



### Specific Energy Consumption
```{r Specific Energy Consumption}
# estimated values for thermodynamic limits are hard coded here. Could be
# improved

# Cement and other non-metallic minerals ----
var1 <- "FE|Industry|Specific Energy Consumption|Cement"
data %>%
  filter(variable == var1) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for cement",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var1,
      value = 1.8)) %>% # GJ/t. # nolint
  showLinePlots(var1)

# Chemicals ----
showLinePlots(data, 'FE|Industry|Specific Energy Consumption|Chemicals')

# Primary steel ----
var2 <- "FE|Industry|Specific Energy Consumption|Primary Steel"
data %>%
  filter(variable == var2) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for primary steel",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var2,
      value = 8.2)) %>% # GJ/t. # nolint
  showLinePlots(var2)

# Secondary steel ----
var3 <- "FE|Industry|Specific Energy Consumption|Secondary Steel"
data %>%
  filter(variable == var3) %>%
  bind_rows(
    expand.grid(
      model = "Thermodynamic limit for secondary steel",
      scenario = "historical",
      region = levels(.$region),
      period = range(.$period),
      variable = var3,
      value = 1.3)) %>% # GJ/t. # nolint
  showLinePlots(var3)

# Other Industry ----
showLinePlots(data, 'FE|Industry|Specific Energy Consumption|Other Industry')
```

## Transport Final Energy

### Basics -- with Bunkers

```{r Transport Final Energy}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Hydrogen",
  "FE|Transport|Gases",
  "FE|Transport|Liquids",
  NULL
)

items2 <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Hydrogen",  
  "FE|Transport|Gases",
  "FE|Transport|Liquids|Biomass",
  "FE|Transport|Liquids|Fossil",
  "FE|Transport|Liquids|Hydrogen",
  NULL
)
```

\newpage

#### FE Transport Area Plots -- with Bunkers

```{r FE Transport Area Plots -- with Bunkers}
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
showAreaAndBarPlots(data, items, tot, orderVars = "user", fill = TRUE)
showAreaAndBarPlots(data, items2, tot, orderVars = "user", scales = "fixed")
```

#### FE Transport Line Plots -- with Bunkers

```{r FE Transport Line Plots -- with Bunkers}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```

#### Electricity Share in Transport Final Energy

```{r Electricity Share in Transport Final Energy}
showLinePlots(data, "FE|Transport|Electricity|Share")
```


### Basics -- w/o Bunkers

```{r Basics -- w/o Bunkers}
tot <- "FE|Transport|w/o Bunkers"
items <- c(
  "FE|Transport|w/o Bunkers|Electricity",
  "FE|Transport|w/o Bunkers|Hydrogen",  
  "FE|Transport|w/o Bunkers|Gases",
  "FE|Transport|w/o Bunkers|Liquids",
  NULL
)
items2 <- c(
  "FE|Transport|w/o Bunkers|Electricity",
  "FE|Transport|w/o Bunkers|Hydrogen",
  "FE|Transport|w/o Bunkers|Gases",
  "FE|Transport|w/o Bunkers|Liquids|Biomass",
  "FE|Transport|w/o Bunkers|Liquids|Fossil",
  "FE|Transport|w/o Bunkers|Liquids|Hydrogen",
  NULL
)
```

\newpage

#### FE Transport Area Plots -- w/o Bunkers

```{r FE Transport Area Plots -- w/o Bunkers}
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
showAreaAndBarPlots(data, items, tot, orderVars = "user", fill = TRUE)
showAreaAndBarPlots(data, items2, tot, orderVars = "user", scales = "fixed")
```

#### FE Transport Line Plots -- w/o Bunkers

```{r FE Transport Line Plots -- w/o Bunkers}
showLinePlots(data, tot)
walk(items, showLinePlots, data = data)
```


### Transport per type

```{r Transport per type}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|LDV|Electricity",
  "FE|Transport|LDV|Hydrogen",
  "FE|Transport|LDV|Gases",
  "FE|Transport|LDV|Liquids",
  "FE|Transport|non-LDV|Electricity",
  "FE|Transport|non-LDV|Hydrogen",
  "FE|Transport|non-LDV|Gases",  
  "FE|Transport|non-LDV|Liquids",
  NULL
)
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```

### Bunkers

```{r FE Transport Bunkers}
tot <- "FE|Transport"
items <- c(
  "FE|Transport|Bunkers",
  "FE|Transport|w/o Bunkers")
showAreaAndBarPlots(data, items, tot, orderVars = "user", scales = "fixed")
```
