# Summary


## GHG Emissions

```{r Emi-GHG}
tot <- "Emi|GHG"
items <- c(
  "Emi|CO2|Energy",
  "Emi|CO2|Industrial Processes",
  "Emi|CO2|Land-Use Change",
  "Emi|GHG|CH4",
  "Emi|GHG|N2O",
  "Emi|GHG|F-Gases",
  "Emi|CO2|non-BECCS CDR")
showAreaAndBarPlots(data, items, tot)
```

## GHG by sector (w/ gross emissions, excl. BECCS)

```{r Emi-GHG with gross}
tot <- "Emi|GHG"
items <- c(
  "Emi|GHG|Gross|Energy|Supply|Electricity",
  "Emi|GHG|Gross|Energy|Supply|Non-electric",
  "Emi|GHG|Energy|Demand|Transport",
  "Emi|GHG|Energy|Demand|Buildings",
  "Emi|GHG|Gross|Energy|Demand|Industry",
  "Emi|GHG|Industrial Processes",
  "Emi|GHG|Agriculture",
  "Emi|GHG|Land-Use Change",
  "Emi|GHG|Waste",
  "Emi|GHG|F-Gas",
  "Emi|CO2|CDR|BECCS",
  "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
  "Emi|CO2|CDR|DACCS",
  "Emi|CO2|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```

## CO2 by sector (w/ gross emissions, excl. BECCS)

```{r CO2 by sector}
tot <- "Emi|CO2"
items <- c(
  "Emi|CO2|Land-Use Change",
  "Emi|CO2|Industrial Processes",
  "Emi|CO2|Energy|Demand|Transport",
  "Emi|CO2|Gross|Energy|Demand|Industry",
  "Emi|CO2|Energy|Demand|Buildings",
  "Emi|CO2|Gross|Energy|Supply|Non-electric",
  "Emi|CO2|Gross|Energy|Supply|Electricity",
  "Emi|CO2|CDR|BECCS",
  "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
  "Emi|CO2|CDR|DACCS",
  "Emi|CO2|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```

```{r CO2 by sector cumulated}
tot <- "Emi|CO2|Cumulated"
items <- c(
  "Emi|CO2|Cumulated|Land-Use Change",
  "Emi|CO2|Cumulated|Industrial Processes",
  "Emi|CO2|Cumulated|Energy|Demand|Transport",
  "Emi|CO2|Cumulated|Energy|Demand|Industry",
  "Emi|CO2|Cumulated|Energy|Demand|Buildings",
  "Emi|CO2|Cumulated|Gross|Energy|Supply|Non-electric",
  "Emi|CO2|Cumulated|Gross|Energy|Supply|Electricity",
  "Emi|CO2|Cumulated|CDR|BECCS",
  "Emi|CO2|Cumulated|CDR|DACCS",
  "Emi|CO2|Cumulated|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```


## FE by sector

```{r FE by sector}
items <- c(
  "FE|CDR",
  "FE|Transport",
  "FE|Buildings",
  "FE|Industry")
showAreaAndBarPlots(data, items)
```

## FE per capita (by sector, time domain, area plot)

```{r FE per capita (by sector, time domain, area plot)}
items <- c(
  "FE|Transport pCap",
	"FE|Buildings pCap",
  "FE|Industry pCap")
showAreaAndBarPlots(data, items)
```

## FE per capita (by sector, time domain, line graph)

```{r FE per capita (by sector, time domain, line graph)}
showMultiLinePlots(data, "FE pCap")
items <- c(
  "FE|Transport pCap",
  "FE|Buildings pCap",
  "FE|Industry pCap")
showMultiLinePlots(data, items)
```

## FE per capita (by sector, GDP)

```{r FE per capita by sector (GDP domain)}
showMultiLinePlotsByGDP(data, "FE pCap")
items <- c(
  "FE|Transport pCap",
	"FE|Buildings pCap",
  "FE|Industry pCap")
showMultiLinePlotsByGDP(data, items)
```

## FE by carrier

```{r FE by carrier}
items <- c(
  "FE|Solids",
  "FE|Liquids",
  "FE|Gases",
  "FE|Heat",
  "FE|Hydrogen",
  "FE|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Industry by carrier

```{r FE Industry by carrier}
items <- c(
  "FE|Industry|Solids",
  "FE|Industry|Liquids",
  "FE|Industry|Gases",
  "FE|Industry|Heat",
  "FE|Industry|Hydrogen",
  "FE|Industry|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Buildings by carrier

```{r FE Buildings by carrier}
items <- c(
  "FE|Buildings|Solids",
  "FE|Buildings|Liquids",
  "FE|Buildings|Gases",
  "FE|Buildings|Heat",
  "FE|Buildings|Hydrogen",
  "FE|Buildings|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Transport by carrier

```{r FE Transport by carrier}
items <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Hydrogen",
  "FE|Transport|Liquids",
  "FE|Transport|Gases")
showAreaAndBarPlots(data, items)
```

## FE CDR by carrier


```{r FE CDR by carrier}
items <- c(
  "FE|CDR|Liquids",
  "FE|CDR|Gases",
  "FE|CDR|Hydrogen",
  "FE|CDR|Electricity")
showAreaAndBarPlots(data, items)
```

## SE Electricity by carrier

```{r SE Electricity by carrier}
items <- c(
  "SE|Electricity|Coal|w/ CCS",
  "SE|Electricity|Coal|w/o CCS",
  "SE|Electricity|Oil",
  "SE|Electricity|Gas|w/ CCS",
  "SE|Electricity|Gas|w/o CCS",
  "SE|Electricity|Geothermal",
  "SE|Electricity|Hydro",
  "SE|Electricity|Nuclear",
  "SE|Electricity|Biomass|w/ CCS",
  "SE|Electricity|Biomass|w/o CCS",
  "SE|Electricity|Solar|CSP",
  "SE|Electricity|Solar|PV",
  "SE|Electricity|Hydrogen",
  "SE|Electricity|Net Imports")

if ("SE|Electricity|Wind|Offshore" %in% variables) {
  items <- c(
    items, 
    "SE|Electricity|Wind|Onshore",
    "SE|Electricity|Wind|Offshore")
} else {
  items <- c(
    items, 
    "SE|Electricity|Wind")
}

showAreaAndBarPlots(data, items)
```




### SE Wind Onshore

```{r SE Wind Onshore}
showLinePlots(data, "SE|Electricity|Wind|Onshore")
```


### SE Wind Offshore

```{r SE Wind Offshore}
showLinePlots(data, "SE|Electricity|Wind|Offshore")
```


## PE by carrier

```{r PE by carrier}
items <- c(
  "PE|Coal",
  "PE|Oil",
  "PE|Gas",
  "PE|Biomass",
  "PE|Nuclear",
  "PE|Solar",
  "PE|Wind",
  "PE|Hydro",
  "PE|Geothermal")
showAreaAndBarPlots(data, items)
```


## CO2 Prices

```{r CO2 Prices}
data %>% 
  filter(variable == "Price|Carbon", scenario != "historical") ->
  d
showLinePlots(d)
d %>% 
  filter(region != mainReg) %>% 
  mipLineHistorical(
    ylab='Price|Carbon [US$2005/t CO2]',
    scales="free_y",
    plot.priority=c("x_hist","x","x_proj"),
    color.dim="region",
    facet.dim="scenario",
    facet.ncol=2) +
  theme(legend.position="right") +
  scale_color_manual(values = plotstyle(regions)) + 
  theme_minimal()
```


```{r CO2 Prices ETS,ESR}
showLinePlots(data, "Price|Carbon|ETS")
showLinePlots(data, "Price|Carbon|ESR")
```


## Policy Costs

```{r Policy Costs-Consumption Loss}
showLinePlots(data, "Policy Cost|Consumption Loss")
```


```{r Policy Cost-Consumption Loss-Relative to Reference Consumption}
showLinePlots(data, "Policy Cost|Consumption Loss|Relative to Reference Consumption")
```


```{r Policy Cost-GDP Loss}
showLinePlots(data, "Policy Cost|GDP Loss")
```

