# Macro


## Consumption

```{r}
showLinePlots(data, "Consumption")
```


## Population

```{r}
showLinePlots(data, "Population")
```

## GDP - MER

```{r}
showLinePlots(data, "GDP|MER")
```

## GDP - PPP

```{r}
showLinePlots(data, "GDP|PPP")
```

## GDP - MER per Capita

```{r}
showLinePlots(data, "GDP|MER pCap")
```

## GDP - PPP per Capita

```{r}
showLinePlots(data, "GDP|PPP pCap")
```



## Capital Stock


```{r}
showLinePlots(data, "Capital Stock|Non-ESM")
```

## Investments

```{r}
showLinePlots(data, "Investments|Non-ESM")
```


## Interest Rate

```{r}
showLinePlots(data, "Interest Rate (t+1)/(t-1)|Real")
```


## GDP Disaggregation

### Top-level GDP Disaggregation

```{r GDP Disaggregation}

tot <- "GDP|MER"
items <- c(
  "Internal|CES Function|Value|lab",
  "Internal|CES Function|Value|kap",
  "Internal|CES Function|Value|entrp",
  "Internal|CES Function|Value|enb",
  "Internal|CES Function|Value|ue_industry")
  
showAreaAndBarPlots(data, items, tot)
```


### Transport Value Disaggregation

```{r Transport Value Disaggregtion}

tot <- "Internal|CES Function|Value|entrp"
items <- c(
  "Internal|CES Function|Value|entrp_pass_sm",
  "Internal|CES Function|Value|entrp_pass_lo",
  "Internal|CES Function|Value|entrp_frgt_sm",
  "Internal|CES Function|Value|entrp_frgt_lo")

showAreaAndBarPlots(data, items, tot)
```

### Buildings Value Disaggregation

```{r Buildings Value Disaggregtion}

tot <- "Internal|CES Function|Value|enb"
items <- c(
  "Internal|CES Function|Value|enhb",
  "Internal|CES Function|Value|feelcb")
  
showAreaAndBarPlots(data, items, tot)
```


### Industry Value Disaggregation

```{r Industry Value Disaggregtion}

tot <- "Internal|CES Function|Value|ue_industry"
items <- c(
  "Internal|CES Function|Value|ue_steel",
  "Internal|CES Function|Value|ue_cement",
  "Internal|CES Function|Value|ue_chemicals",
  "Internal|CES Function|Value|ue_otherInd")
  
showAreaAndBarPlots(data, items, tot)
```



## Prices

```{r}
# Local (this subsection) preprocessing for all price variables.
dPrice <-
  data %>%
    filter(scenario != "historical") %>%
    filter(str_starts(variable, "Price")) %>%
    filter(period >= 2010) %>% # 2005 values are invalid
    droplevels()
```


### PE Prices

```{r}
vars <-
  levels(dPrice$variable) %>%
  str_subset("^Price\\|Primary Energy\\|") %>%
  str_subset("\\|Moving Avg$", negate = TRUE)
walk(vars, showLinePlots, data = dPrice, scale = "fixed")
```

### SE Prices


```{r}
vars <-
  levels(dPrice$variable) %>%
  str_subset("^Price\\|Secondary Energy\\|") %>%
  str_subset("\\|Moving Avg$", negate = TRUE)
walk(vars, showLinePlots, data = dPrice, scale = "fixed")
```

### FE Prices

```{r}
vars <-
levels(dPrice$variable) %>%
  str_subset("^Price\\|Final Energy\\|") %>%
  str_subset(
    "\\|Moving Avg|\\|Total LCOE|\\|Fuel Cost|\\|Transport and Distribution|\\|Carbon Price Component|\\|Other Taxes$",
    negate = TRUE)

vars %>%
  str_subset("Liquids") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
vars %>%
  str_subset("Gases") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
vars %>%
  str_subset("Solids") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
vars %>%
  str_subset("Electricity") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
vars %>%
  str_subset("Hydrogen") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
vars %>%
  str_subset("Heat") %>%
  walk(showLinePlots, data = dPrice, scale = "fixed")
``` 

### FE LCOE Prices Transport

```{r}

groups <- c(
  "Price|Final Energy|Transport|Liquids|Petroleum",
  "Price|Final Energy|Transport|Liquids|Diesel",
  "Price|Final Energy|Transport|Liquids|Biomass",
  "Price|Final Energy|Transport|Liquids|Efuel",
  "Price|Final Energy|Transport|Gases|Natural Gas",
  "Price|Final Energy|Transport|Gases|Efuel",
  "Price|Final Energy|Transport|Electricity",
  "Price|Final Energy|Transport|Hydrogen"
)

for (g in groups) {

  items <- c(
    paste0(g, "|Fuel Cost"),
    paste0(g, "|Transport and Distribution"),
    paste0(g, "|Carbon Price Component"),
    paste0(g, "|Other Taxes")
  )

  tot <- paste0(g, "|Total LCOE")

  showAreaAndBarPlots(dPrice, intersect(items, unique(dPrice$variable)), tot)
}
```

### FE LCOE Prices Buildings

```{r}

groups <- c(
  "Price|Final Energy|Buildings|Liquids|Oil",
  "Price|Final Energy|Buildings|Liquids|Biomass",
  "Price|Final Energy|Buildings|Liquids|Efuel",
  "Price|Final Energy|Buildings|Gases|Natural Gas",
  "Price|Final Energy|Buildings|Gases|Biomass",
  "Price|Final Energy|Buildings|Gases|Efuel",
  "Price|Final Energy|Buildings|Solids|Biomass",
  "Price|Final Energy|Buildings|Electricity",
  "Price|Final Energy|Buildings|Heat",
  "Price|Final Energy|Buildings|Hydrogen"
)

for (g in groups) {

  items <- c(
    paste0(g, "|Fuel Cost"),
    paste0(g, "|Transport and Distribution"),
    paste0(g, "|Carbon Price Component"),
    paste0(g, "|Other Taxes")
  )

  tot <- paste0(g, "|Total LCOE")

  showAreaAndBarPlots(dPrice, intersect(items, unique(dPrice$variable)), tot)
}
```

### FE LCOE Prices Industry

```{r}

groups <- c(
  "Price|Final Energy|Industry|Liquids|Oil",
  "Price|Final Energy|Industry|Liquids|Biomass",
  "Price|Final Energy|Industry|Liquids|Efuel",
  "Price|Final Energy|Industry|Gases|Natural Gas",
  "Price|Final Energy|Industry|Gases|Biomass",
  "Price|Final Energy|Industry|Gases|Efuel",
  "Price|Final Energy|Industry|Solids|Coal",
  "Price|Final Energy|Industry|Solids|Biomass",
  "Price|Final Energy|Industry|Electricity",
  "Price|Final Energy|Industry|Heat",
  "Price|Final Energy|Industry|Hydrogen"
)

for (g in groups) {

  items <- c(
    paste0(g, "|Fuel Cost"),
    paste0(g, "|Transport and Distribution"),
    paste0(g, "|Carbon Price Component"),
    paste0(g, "|Other Taxes")
  )

  tot <- paste0(g, "|Total LCOE")

  showAreaAndBarPlots(dPrice, intersect(items, unique(dPrice$variable)), tot)
}
```

## Trade

```{r}
vars <-
  levels(data$variable) %>%
  str_subset("^Trade\\|[^|]*$")
walk(vars, showLinePlots, data = data)
```

## FE intensity of GDP

```{r}
items <- c(
  "FE|Transport pGDP",
  "FE|Buildings pGDP",
  "FE|Industry pGDP")
showAreaAndBarPlots(data, items)
```

## FE intensity of GDP, linegraph (by GDP)

```{r}
dIea <-
  data %>%
  # To make the plots less crowded, show only IEA historical data.
  filter(scenario != "historical" | model == "IEA")
items <- c(
  "FE|Transport pGDP",
  "FE|Buildings pGDP",
  "FE|Industry pGDP")
showMultiLinePlots(dIea, items, scales = "fixed")
showMultiLinePlotsByVariable(dIea, items, "GDP|PPP pCap", scales = "fixed")
```

## Kaya-Decomposition

```{r}
d <-
  data %>%
  filter(variable %in% c("Emi|CO2|Energy", "FE", "GDP|MER", "Population")) %>%
  filter(scenario != "historical") %>%
  select(model, scenario, region, variable, unit, period, value)
oldUnits <-
  d %>%
  distinct(variable, unit)
kaya <-
  d %>%
  select(-unit) %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  mutate(
    emiCO2_by_FE = `Emi|CO2|Energy` / FE,
    FE_by_GDP = FE / `GDP|MER`,
    GDP_by_Pop = `GDP|MER` / Population,
    `Emi|CO2|Energy` = NULL, FE = NULL, `GDP|MER` = NULL) %>%
  pivot_longer(
    c(emiCO2_by_FE, FE_by_GDP, GDP_by_Pop, Population),
    names_to = "variable",
    values_to = "value")
kayaUnits <- tribble(
  ~variable, ~unit,
  "Population", "million",
  "GDP_by_Pop", "billion US$2005/yr/million",
  "FE_by_GDP", "EJ/billion US$2005",
  "emiCO2_by_FE", "EJ/Mt CO2")
kayaVars <- kayaUnits$variable
kaya <-
  kaya %>%
  left_join(kayaUnits, by = "variable") %>%
  as.quitte()

refYear <- getOption("kaya.refYear")
kayaRef <-
  kaya %>%
  filter(period == refYear) %>%
  select(-period) %>%
  rename(refValue = value)
kayaRel <-
  kaya %>%
  left_join(kayaRef, by = c("model", "scenario", "region", "variable", "unit")) %>%
  mutate(
    value = value / refValue,
    unit = paste0("relative to ", refYear),
    refValue = NULL) %>%
  as.quitte()
```

### Absolute

```{r}
showMultiLinePlots(kaya, kayaVars)
walk(kayaVars, showRegiLinePlots, data = kaya)
```

```{r results='asis'}
cat("### Relative to ", refYear, "\n")
```

```{r}
showMultiLinePlots(kayaRel, kayaVars)
walk(kayaVars, showRegiLinePlots, data = kayaRel)
```

### Components

```{r}
walk(kayaVars, showLinePlots, data = kaya)
```
