# Energy Supply

## Investments Electricity

```{r}
items <- c(
#  "Energy Investments|Elec|Grid",
  "Energy Investments|Elec|Grid|BEV Chargers",
  "Energy Investments|Elec|Grid|VRE support",
  "Energy Investments|Elec|Grid|Normal",
  "Energy Investments|Elec|Hydrogen",
  "Energy Investments|Elec|Storage",
  "Energy Investments|Elec|Solar",
  "Energy Investments|Elec|Wind",
  "Energy Investments|Elec|Geothermal",
  "Energy Investments|Elec|Hydro",
  "Energy Investments|Elec|Biomass|w/ CC",
  "Energy Investments|Elec|Biomass|w/o CC",
  "Energy Investments|Elec|Oil",
  "Energy Investments|Elec|Gas|w/ CC",
  "Energy Investments|Elec|Gas|w/o CC",
  "Energy Investments|Elec|Coal|w/ CC",
  "Energy Investments|Elec|Coal|w/o CC",
  "Energy Investments|Elec|Nuclear")
showAreaAndBarPlots(data, items, orderVars = "user")
```

## Capacities Electricity

```{r}
items <- c(
  "Cap|Electricity|Storage|Battery",
  "Cap|Electricity|Solar",
  if ("Cap|Electricity|Wind|Offshore" %in% levels(data$variable))
    c("Cap|Electricity|Wind|Onshore", "Cap|Electricity|Wind|Offshore")
  else
    "Cap|Electricity|Wind",
  "Cap|Electricity|Hydro",
  "Cap|Electricity|Geothermal",
  "Cap|Electricity|Biomass",
  "Cap|Electricity|Hydrogen",
  "Cap|Electricity|Gas|w/ CC",
  "Cap|Electricity|Gas|w/o CC",
  "Cap|Electricity|Oil|w/o CC",
  "Cap|Electricity|Coal|w/ CC",
  "Cap|Electricity|Coal|w/o CC",
  "Cap|Electricity|Nuclear"
  )
showAreaAndBarPlots(data, items, orderVars = "user")
```

## Capacities electricity line plots

### Nuclear
```{r}
showLinePlots(data, "Cap|Electricity|Nuclear")
```

### Hydro
```{r}
showLinePlots(data, "Cap|Electricity|Hydro")
```

### Wind
```{r}
showLinePlots(data, "Cap|Electricity|Wind")
showLinePlots(data, "Cap|Electricity|Wind|Onshore")
showLinePlots(data, "Cap|Electricity|Wind|Offshore")
```

### Solar
```{r}
showLinePlots(data, "Cap|Electricity|Solar")
```

### Coal
```{r}
showLinePlots(data, "Cap|Electricity|Coal")
```

### Coal
```{r}
showLinePlots(data, "Cap|Electricity|Gas")
```

### Oil
```{r}
showLinePlots(data, "Cap|Electricity|Oil")
```

### Biomass
```{r}
showLinePlots(data, "Cap|Electricity|Biomass")
```

### Hydrogen
```{r}
showLinePlots(data, "Cap|Electricity|Hydrogen")
```

## PE Mix
### PE|Coal
```{r}
items <- c(
  "PE|Coal|Gases",
  "PE|Coal|Liquids",
  "PE|Coal|Solids",
  "PE|Coal|Heat",
  "PE|Coal|Electricity",
  "PE|Coal|Hydrogen")
showAreaAndBarPlots(data, items)
```

### PE|Gas
```{r}
items <- c(
  "PE|Gas|Gases",
  "PE|Gas|Heat",
  "PE|Gas|Electricity|w/ CC",
  "PE|Gas|Electricity|w/o CC",
  "PE|Gas|Liquids|w/ CC",
  "PE|Gas|Liquids|w/o CC",
  "PE|Gas|Hydrogen|w/ CC",
  "PE|Gas|Hydrogen|w/o CC")
showAreaAndBarPlots(data, items)
```


### PE|Biomass

```{r}
items <- c(
  "PE|Biomass|Solids",
  "PE|Biomass|Heat",
  "PE|Biomass|Liquids|w/ CC",
  "PE|Biomass|Liquids|w/o CC",
  "PE|Biomass|Gases",
  "PE|Biomass|Electricity|w/ CC",
  "PE|Biomass|Electricity|w/o CC",
  "PE|Biomass|Hydrogen|w/ CC",
  "PE|Biomass|Hydrogen|w/o CC")
showAreaAndBarPlots(data, items)
```

## Primary Energy line plots

```{r}
showLinePlots(data, "PE|Coal")
showLinePlots(data, "PE|Oil")
showLinePlots(data, "PE|Gas")
showLinePlots(data, "PE|Biomass")
showLinePlots(data, "Primary Energy Production|Biomass|Energy Crops")
```

### PE|Coal|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Coal")
```

### PE|Oil|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Oil")
```

### PE|Gas|Extraction
```{r}
showLinePlots(data, "Res|Extraction|Gas")
```

## Secondary Energy Mixes


### SE Electricity

```{r}

tot <- "SE|Electricity"

items <- c(
  "SE|Electricity|Coal|w/ CC",
  "SE|Electricity|Coal|w/o CC",
  "SE|Electricity|Oil",
  "SE|Electricity|Gas|w/ CC",
  "SE|Electricity|Gas|w/o CC",
  "SE|Electricity|Geothermal",
  "SE|Electricity|Hydro",
  "SE|Electricity|Nuclear",
  "SE|Electricity|Biomass|w/ CC",
  "SE|Electricity|Biomass|w/o CC",
  "SE|Electricity|Solar|CSP",
  "SE|Electricity|Solar|PV",
  "SE|Electricity|Wind|Onshore",
  "SE|Electricity|Wind|Offshore",
  "SE|Electricity|Hydrogen",
  "SE|Electricity|Net Imports")

showAreaAndBarPlots(data, items, tot)
```



### SE|Electricity - Usage
```{r}

tot <- "SE|Electricity"

items <- c(
  "SE|Input|Electricity|Hydrogen|Synthetic Fuels|Liquids",
  "SE|Input|Electricity|Hydrogen|Synthetic Fuels|Gases",
  "SE|Input|Electricity|Hydrogen|direct FE H2",
  "SE|Input|Electricity|Hydrogen|Electricity Storage",
  "SE|Input|Electricity|Buildings",
  "SE|Input|Electricity|Industry",
  "SE|Input|Electricity|Transport",
  "SE|Input|Electricity|CDR",
  "SE|Input|Electricity|Self Consumption Energy System")

showAreaAndBarPlots(data, items, tot)
```


### SE|Heat
```{r}
tot <- "SE|Heat"
items <- c(
  "SE|Heat|Biomass",
  "SE|Heat|Coal",
  "SE|Heat|Gas",
  "SE|Heat|Electricity|Heat Pump")
showAreaAndBarPlots(data, items, tot)
```


### SE|Hydrogen
```{r}

tot <- "SE|Hydrogen"

items <- c(
  "SE|Hydrogen|Biomass|w/ CC",
  "SE|Hydrogen|Biomass|w/o CC",
  "SE|Hydrogen|Coal|w/ CC",
  "SE|Hydrogen|Coal|w/o CC",
  "SE|Hydrogen|Gas|w/ CC",
  "SE|Hydrogen|Gas|w/o CC",
  "SE|Hydrogen|Electricity|VRE Storage Electrolysis",
  "SE|Hydrogen|Electricity|Standard Electrolysis",
  "SE|Hydrogen|Net Imports")
showAreaAndBarPlots(data, items, tot)
```

### SE|Hydrogen - Usage
```{r}

tot <- "SE|Hydrogen"

items <- c(
  "FE|Industry|Hydrogen",
  "FE|Buildings|Hydrogen",
  "FE|Transport|Hydrogen",
  "FE|CDR|Hydrogen",
  "SE|Input|Hydrogen|Electricity|Normal Turbines",
  "SE|Input|Hydrogen|Electricity|Forced VRE Turbines",
  "SE|Input|Hydrogen|Synthetic Fuels|Liquids",
  "SE|Input|Hydrogen|Synthetic Fuels|Gases")
showAreaAndBarPlots(data, items, tot)
```



### SE|Solids
```{r}

tot <- "SE|Solids"

items <- c(
  "SE|Solids|Biomass",
  "SE|Solids|Traditional Biomass",
  "SE|Solids|Coal")
showAreaAndBarPlots(data, items, tot)
```


### SE|Liquids

```{r}

tot <- "SE|Liquids"

items <- c(
  "SE|Liquids|Fossil|Oil",
  "SE|Liquids|Biomass|w/ CC",
  "SE|Liquids|Biomass|w/o CC",
  "SE|Liquids|Fossil|Coal|w/ CC",
  "SE|Liquids|Fossil|Coal|w/o CC",
  "SE|Liquids|Fossil|Gas|w/ CC",
  "SE|Liquids|Fossil|Gas|w/o CC",
  "SE|Liquids|Hydrogen",
  "SE|Liquids|Hydrogen|Net Imports")
showAreaAndBarPlots(data, items, tot)
```

### SE|Gases
```{r}

tot <- "SE|Gases"

items <- c(
  "SE|Gases|Fossil|Natural Gas",
  "SE|Gases|Biomass|w/ CC",
  "SE|Gases|Biomass|w/o CC",
  "SE|Gases|Fossil|Coal|w/ CC",
  "SE|Gases|Fossil|Coal|w/o CC",
  "SE|Gases|Hydrogen",
  "SE|Gases|Waste")
showAreaAndBarPlots(data, items, tot)
```






## Secondary Energy line plots - totals

### SE|Electricity
```{r}
showLinePlots(data, "SE|Electricity")
```

### SE|Heat
```{r}
showLinePlots(data, "SE|Heat")
```

### SE|Hydrogen
```{r}
showLinePlots(data, "SE|Hydrogen")
```


### SE|Solids
```{r}
showLinePlots(data, "SE|Solids")
```


### SE|Liquids
```{r}
showLinePlots(data, "SE|Liquids")
```

### SE|Gases
```{r}
showLinePlots(data, "SE|Gases")
```




## Secondary Energy line plots - detail


### SE|Electricity
```{r}
showLinePlots(data, "SE|Electricity|Gas")
showLinePlots(data, "SE|Electricity|Coal")
showLinePlots(data, "SE|Electricity|Oil")
showLinePlots(data, "SE|Electricity|Nuclear")
showLinePlots(data, "SE|Electricity|Hydro")
showLinePlots(data, "SE|Electricity|Hydrogen")
showLinePlots(data, "SE|Electricity|Wind")
showLinePlots(data, "SE|Electricity|Wind|Onshore")
showLinePlots(data, "SE|Electricity|Wind|Offshore")
showLinePlots(data, "SE|Electricity|Solar")
showLinePlots(data, "SE|Electricity|Solar|PV")
showLinePlots(data, "SE|Electricity|Solar|CSP")
showLinePlots(data, "SE|Electricity|Biomass")
```


### SE|Heat
```{r}

showLinePlots(data, "SE|Heat|Coal")
showLinePlots(data, "SE|Heat|Gas")
showLinePlots(data, "SE|Heat|Biomass")
showLinePlots(data, "SE|Heat|Electricity|Heat Pump")

```

### SE|Hydrogen
```{r}

showLinePlots(data,  "SE|Hydrogen|Biomass|w/ CC")
showLinePlots(data,  "SE|Hydrogen|Biomass|w/o CC")
showLinePlots(data,  "SE|Hydrogen|Coal|w/ CC")
showLinePlots(data,  "SE|Hydrogen|Coal|w/o CC")
showLinePlots(data,  "SE|Hydrogen|Electricity|VRE Storage Electrolysis")
showLinePlots(data,  "SE|Hydrogen|Electricity|Standard Electrolysis")
showLinePlots(data,  "SE|Hydrogen|Gas|w/ CC")
showLinePlots(data,  "SE|Hydrogen|Gas|w/o CC")
showLinePlots(data,  "SE|Hydrogen|Net Imports")

```

### SE|Solids
```{r}
showLinePlots(data, "SE|Solids|Coal")
showLinePlots(data, "SE|Solids|Biomass")
showLinePlots(data, "SE|Solids|Traditional Biomass")
```

### SE|Liquids

```{r}


showLinePlots(data, "SE|Liquids|Fossil|Oil")
showLinePlots(data, "SE|Liquids|Fossil|Coal|w/ CC")
showLinePlots(data, "SE|Liquids|Fossil|Coal|w/o CC")
showLinePlots(data, "SE|Liquids|Fossil|Gas|w/ CC")
showLinePlots(data, "SE|Liquids|Fossil|Gas|w/o CC")
showLinePlots(data, "SE|Liquids|Biomass|w/ CC")
showLinePlots(data, "SE|Liquids|Biomass|w/o CC")
showLinePlots(data, "SE|Liquids|Hydrogen")


```


### SE|Gases
```{r}
showLinePlots(data,  c("SE|Gases|Fossil|Natural Gas", "SE|Gases|Gas"))
showLinePlots(data, "SE|Gases|Fossil|Coal")
showLinePlots(data, "SE|Gases|Biomass")
showLinePlots(data, "SE|Gases|Waste")

```
