# Summary



## GHG Emissions

```{r}
tot <- "Emi|GHG"
items <- c(
  "Emi|CO2|Energy",
  "Emi|CO2|Industrial Processes",
  "Emi|CO2|Land-Use Change",
  "Emi|GHG|CH4",
  "Emi|GHG|N2O",
  "Emi|GHG|F-Gases",
  "Emi|CO2|non-BECCS CDR")
showAreaAndBarPlots(data, items, tot)
```

## GHG by sector (w/ gross emissions, excl. BECCS)

```{r}
tot <- "Emi|GHG"
items <- c(
  "Emi|GHG|Gross|Energy|Supply|Electricity",
  "Emi|GHG|Gross|Energy|Supply|Non-electric",
  "Emi|GHG|Energy|Demand|Transport",
  "Emi|GHG|Energy|Demand|Buildings",
  "Emi|GHG|Gross|Energy|Demand|Industry",
  "Emi|GHG|Industrial Processes",
  "Emi|GHG|Agriculture",
  "Emi|GHG|Land-Use Change",
  "Emi|GHG|Waste",
  "Emi|CO2|CDR|BECCS",
  "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
  "Emi|CO2|CDR|DACCS",
  "Emi|CO2|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```

### GHG pCap by sector

```{r}
showAreaAndBarPlots(data, paste(items, "pCap"), paste(tot, "pCap"))
```

## CO2 by sector (w/ gross emissions, excl. BECCS)

```{r}
tot <- "Emi|CO2"
items <- c(
  "Emi|CO2|Land-Use Change",
  "Emi|CO2|Industrial Processes",
  "Emi|CO2|Energy|Demand|Transport",
  "Emi|CO2|Gross|Energy|Demand|Industry",
  "Emi|CO2|Energy|Demand|Buildings",
  "Emi|CO2|Gross|Energy|Supply|Non-electric",
  "Emi|CO2|Gross|Energy|Supply|Electricity",
  "Emi|CO2|CDR|BECCS",
  "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
  "Emi|CO2|CDR|DACCS",
  "Emi|CO2|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```

###  CO2 pCap by sector

```{r}
showAreaAndBarPlots(data, paste(items, "pCap"), paste(tot, "pCap"))
```


###  CO2 cumulated by sector

```{r}
tot <- "Emi|CO2|Cumulated"
items <- c(
  "Emi|CO2|Cumulated|Land-Use Change",
  "Emi|CO2|Cumulated|Industrial Processes",
  "Emi|CO2|Cumulated|Energy|Demand|Transport",
  "Emi|CO2|Cumulated|Energy|Demand|Industry",
  "Emi|CO2|Cumulated|Energy|Demand|Buildings",
  "Emi|CO2|Cumulated|Gross|Energy|Supply|Non-electric",
  "Emi|CO2|Cumulated|Gross|Energy|Supply|Electricity",
  "Emi|CO2|Cumulated|CDR|BECCS",
  "Emi|CO2|Cumulated|CDR|DACCS",
  "Emi|CO2|Cumulated|CDR|EW")
showAreaAndBarPlots(data, items, tot)
```


## FE by sector

```{r}
items <- c(
  "FE|CDR",
  "FE|Transport",
  "FE|Buildings",
  "FE|Industry")
showAreaAndBarPlots(data, items)
```

## FE per capita (by sector, time domain, area plot)

```{r}
items <- c(
  "FE|Transport pCap",
  "FE|Buildings pCap",
  "FE|Industry pCap")
showAreaAndBarPlots(data, items)
```

## FE per capita (by sector, time domain, line graph)

```{r}
dIea <- data %>%
  # To make the plots less crowded, show only IEA historical data.
  filter(scenario != "historical" | model == "IEA")
showMultiLinePlots(dIea, "FE pCap")
items <- c(
  "FE|Transport pCap",
  "FE|Buildings pCap",
  "FE|Industry pCap")
showMultiLinePlots(dIea, items, scales = "fixed")
```

## FE per capita (by sector, GDP)

```{r}
dIea <- data %>%
  # To make the plots less crowded, show only IEA historical data.
  filter(scenario != "historical" | model == "IEA")
showMultiLinePlotsByVariable(dIea, "FE pCap", "GDP|PPP pCap")
items <- c(
  "FE|Transport pCap",
  "FE|Buildings pCap",
  "FE|Industry pCap")
showMultiLinePlotsByVariable(dIea, items, "GDP|PPP pCap", scales = "fixed")
```

## FE by carrier

```{r}
items <- c(
  "FE|Solids",
  "FE|Liquids",
  "FE|Gases",
  "FE|Heat",
  "FE|Hydrogen",
  "FE|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Industry by carrier

```{r}
items <- c(
  "FE|Industry|Solids",
  "FE|Industry|Liquids",
  "FE|Industry|Gases",
  "FE|Industry|Heat",
  "FE|Industry|Hydrogen",
  "FE|Industry|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Buildings by carrier

```{r}
items <- c(
  "FE|Buildings|Solids",
  "FE|Buildings|Liquids",
  "FE|Buildings|Gases",
  "FE|Buildings|Heat",
  "FE|Buildings|Hydrogen",
  "FE|Buildings|Electricity")
showAreaAndBarPlots(data, items)
```

## FE Transport by carrier

```{r}
items <- c(
  "FE|Transport|Electricity",
  "FE|Transport|Hydrogen",
  "FE|Transport|Liquids",
  "FE|Transport|Gases")
showAreaAndBarPlots(data, items)
```

## FE CDR by carrier


```{r}
items <- c(
  "FE|CDR|Liquids",
  "FE|CDR|Gases",
  "FE|CDR|Hydrogen",
  "FE|CDR|Electricity")
showAreaAndBarPlots(data, items)
```

## SE Electricity by carrier

```{r}
items <- c(
  "SE|Electricity|Coal|w/ CC",
  "SE|Electricity|Coal|w/o CC",
  "SE|Electricity|Oil",
  "SE|Electricity|Gas|w/ CC",
  "SE|Electricity|Gas|w/o CC",
  "SE|Electricity|Geothermal",
  "SE|Electricity|Hydro",
  "SE|Electricity|Nuclear",
  "SE|Electricity|Biomass|w/ CC",
  "SE|Electricity|Biomass|w/o CC",
  "SE|Electricity|Solar|CSP",
  "SE|Electricity|Solar|PV",
  "SE|Electricity|Hydrogen",
  "SE|Electricity|Net Imports")

if ("SE|Electricity|Wind|Offshore" %in% levels(data$variable)) {
  items <- c(
    items,
    "SE|Electricity|Wind|Onshore",
    "SE|Electricity|Wind|Offshore")
} else {
  items <- c(
    items,
    "SE|Electricity|Wind")
}

showAreaAndBarPlots(data, items)
```




### SE Wind Onshore

```{r}
showLinePlots(data, "SE|Electricity|Wind|Onshore")
```


### SE Wind Offshore

```{r}
showLinePlots(data, "SE|Electricity|Wind|Offshore")
```


## PE by carrier

```{r}
items <- c(
  "PE|Coal",
  "PE|Oil",
  "PE|Gas",
  "PE|Biomass",
  "PE|Nuclear",
  "PE|Solar",
  "PE|Wind",
  "PE|Hydro",
  "PE|Geothermal")
showAreaAndBarPlots(data, items)
```


## CO2 Prices

```{r}
showLinePlots(data, "Price|Carbon")
showRegiLinePlots(data, "Price|Carbon")
```

```{r}
items <- c(
  "Price|Carbon|Demand|Transport",
  "Price|Carbon|Demand|Buildings",
  "Price|Carbon|Demand|Industry",
  "Price|Carbon|Supply"
)
# older runs might not have the new sector tax variables
if (all(items %in% data$variable)) {
  avgTax <- data[data$variable == "Price|Carbon"                  & data$scenario != "historical", "value"]
  buiTax <- data[data$variable == "Price|Carbon|Demand|Buildings" & data$scenario != "historical", "value"]
  traTax <- data[data$variable == "Price|Carbon|Demand|Transport" & data$scenario != "historical", "value"]
  indTax <- data[data$variable == "Price|Carbon|Demand|Industry"  & data$scenario != "historical", "value"]
  supTax <- data[data$variable == "Price|Carbon|Supply"           & data$scenario != "historical", "value"]
  # only create plots if a tax is unequal to the average co2 tax
  if (!identical(buiTax, avgTax) ||
      !identical(traTax, avgTax) ||
      !identical(indTax, avgTax) ||
      !identical(supTax, avgTax)
      ) {
    showLinePlots(data, "Price|Carbon|Demand|Buildings")
    showLinePlots(data, "Price|Carbon|Demand|Transport")
    showLinePlots(data, "Price|Carbon|Demand|Industry")
    showLinePlots(data, "Price|Carbon|Supply")
  }
}
```

```{r}
showLinePlots(data, "Price|Carbon|ETS")
showLinePlots(data, "Price|Carbon|ESR")
```


## Policy Costs

```{r}
showLinePlots(data, "Policy Cost|Consumption Loss")
```


```{r}
showLinePlots(data, "Policy Cost|Consumption Loss|Relative to Reference Consumption")
```


```{r}
showLinePlots(data, "Policy Cost|GDP Loss")
```

## Tables of Significant Periods 

Every statistic in the following tables, e.g., $\max$, $\min$, is taken over the REMIND model outputs only (no historical data).

\newpage

### Emi|CO2: Max, Min, and Net 0

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|CO2",
    stats = list("Max Period (Max Value)" = function(v, p) {
      sprintf("%d (%5.2f)", p[which.max(v)], max(v) / 1000)
    })
  ) %>%
  mutate(unit = "Gt CO2/yr") %>% # divided by 1000 and change unit form Mt to Gt
  showStatsTable()
```

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|CO2",
    stats = list("Min Period (Min Value)" = function(v, p) {
      sprintf("%d (%5.2f)", p[which.min(v)], min(v) / 1000)
    })
  ) %>%
  mutate(unit = "Gt CO2/yr") %>% # divided by 1000 and change unit form Mt to Gt
  showStatsTable()
```

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|CO2",
    stats = list("Net 0 Period, i.e., first period with < 2\\% of 2005 value" = function(v, p) {
      p[which(v <= v[p == 2005] * 0.02)[1]]
    })
  ) %>%
  showStatsTable()
```

\newpage

### Emi|GHG: Max, Min, and Net 0

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|GHG",
    stats = list("Max Period (Max Value)" = function(v, p) {
      sprintf("%d (%5.2f)", p[which.max(v)], max(v) / 1000)
    })
  ) %>%
  mutate(unit = "Gt CO2eq/yr") %>% # divided by 1000 and change unit form Mt to Gt
  showStatsTable()
```

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|GHG",
    stats = list("Min Period (Min Value)" = function(v, p) {
      sprintf("%d (%5.2f)", p[which.min(v)], min(v) / 1000)
    })
  ) %>%
  mutate(unit = "Gt CO2eq/yr") %>% # divided by 1000 and change unit form Mt to Gt
  showStatsTable()
```

```{r}
data %>%
  calcTimeSeriesStats(
    "Emi|GHG",
    stats = list("Net 0 Period, i.e., first period with < 2\\% of 2005 value" = function(v, p) {
      p[which(v <= v[p == 2005] * 0.02)[1]]
    })
  ) %>%
  showStatsTable()
```

\newpage


### Temperature|Global Mean: Max

```{r}
data %>%
  calcTimeSeriesStats(
    "Temperature|Global Mean",
    stats = list("Max Period (Max Value)" = function(v, p) {
      sprintf("%d (%.2f)", p[which.max(v)], max(v))
    })
  ) %>%
  showStatsTable()
```

\newpage

