# Carbon Management

## Carbon Capture
### Capture Total - Line
```{r Capture Total - Line}
showLinePlots(data, "Carbon Management|Carbon Capture")
```

### Capture by type - Bar
```{r Capture by type - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Carbon Capture", scales = "fixed")
```

### Bio PE2SE Capture by carrier - Bar
```{r Bio PE2SE Capture by carrier - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Carbon Capture|Biomass|Pe2Se", scales = "fixed")
```

### Fossil PE2SE Capture by carrier - Bar
```{r Fossil PE2SE Capture by carrier - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Carbon Capture|Fossil|Pe2Se", scales = "fixed")
```

### Industry Energy Capture by PE - Bar
```{r Industry Energy Capture by PE - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Carbon Capture|Industry Energy", scales = "fixed")
```

### Industry Process Capture by sector - Bar
```{r Industry Process Capture by sector - Bar}
showAreaAndBarPlots(
  data = data,
  vars = rev(c('Carbon Management|Carbon Capture|Industry Energy|Cement',
               'Carbon Management|Carbon Capture|Industry Process|Cement',
               'Carbon Management|Carbon Capture|Industry Energy|Chemicals',
               'Carbon Management|Carbon Capture|Industry Energy|Steel')),
  scales = 'fixed',
  orderVars = 'user')
```

## Split Usage / Storage
### Share of Storage in Capture - Line
```{r Share of Storage in Capture}
showLinePlots(data, "Carbon Management|Share of Stored CO2 from Captured CO2")
```

### Use of captured carbon - Bar
```{r Use of captured carbon - Bar}
showAreaAndBarPlots(data, 
                    vars = c('Carbon Management|Storage',
                             'Carbon Management|Usage'),
                    tot = 'Carbon Management|Carbon Capture')
```

## Carbon Storage
### Storage Total - Line
```{r Storage Total - Line}
showLinePlots(data, "Carbon Management|Storage")
```

### Storage by source type - Bar
```{r Storage by source type - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Storage", scales = "fixed")
```

### Storage from Industry Energy by PE - Bar
```{r Storage from Industry Energy by PE - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Storage|Industry Energy", scales = "fixed")
```

### Share of storage potential used
```{r Share of storage potential used}
showLinePlots(data, "Carbon Management|Storage|Share of annual potential used")
```

### Maximum annual storage
```{r Maximum annual storage}
showAreaAndBarPlots(data,
                    vars = c("Carbon Management|Storage"),
                    tot = "Carbon Management|Storage|Maximum annual CO2 storage potential")
```

## Carbon Usage
### Usage Total - Line
```{r Usage Total - Line}
showLinePlots(data, "Carbon Management|Usage")
```

### Usage for carrier - Bar
```{r Usage for carrier - Bar}
showAreaAndBarPlotsPlus(data, "Carbon Management|Usage", scales = "fixed")
```


# Materials

## Total plastics production
```{r }
showLinePlots(data, "Carbon Management|Materials|Plastics")
```

## Plastics production by origin
```{r }
showAreaAndBarPlots(data, 
                        vars = c("Carbon Management|Materials|Plastics|Fossil",
                                 "Carbon Management|Materials|Plastics|Biomass",
                                 "Carbon Management|Materials|Plastics|Synfuels"), 
                        scales = "fixed")
```

## Plastic waste by fate
```{r }
showAreaAndBarPlots(data, 
                        vars = c("Carbon Management|Materials|Plastics|Waste|Incineration",
                                 "Carbon Management|Materials|Plastics|Waste|Other destination"), 
                        scales = "fixed")
```
