---
title: "Compare calibration targets"
date: "`r format(Sys.Date())`"
output:
  html_document:
    toc: no
    keep_tex: false
geometry: "a4paper,landscape,left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm,footnotesep=0.0cm,footskip=0.1cm"
params:
  gdxPaths: ""
  gdxPathNames: null
  figWidth: 16 
  figHeight: 9
  warning: no
  message: no
---

<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  img {
    max-width: 100% !important;
    display: block !important;
    margin-left: auto !important;
    margin-right: auto !important;
  }
</style>

```{r setup, include=FALSE}
library(svglite) # nolint

knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  message = params$message,
  warning = params$warning,
  fig.width = params$figWidth,
  fig.height = params$figHeight,
  dev = "svglite",
  fig.ext = ".svg",
  dpi = 100
)
```


```{r libraries, include=FALSE}
# kableExtra must not be loaded before the call of library(kableExtra) below,
# as its .onLoad() function must be called to tell knitr about add necessary
# LaTeX libraries needed for tables.
# If the following line is not included, successive calls to compareScenarios2()
# may cause "Undefined control sequence" errors in LaTeX.
try(unloadNamespace("kableExtra"), silent = TRUE)

library(kableExtra) # nolint
library(quitte) # nolint
library(gdx) # nolint
library(ggplot2) # nolint
library(dplyr) # nolint
library(madrat) # nolint
```


```{r read, include=FALSE}
data <- NULL
for (i in seq(length(params$gdxPaths))) {
  tmp <- readGDX(params$gdxPaths[[i]], "pm_cesdata", restore_zeros = FALSE)[, , "quantity"] %>% dimReduce()
  if (!is.null(params$gdxPathNames)) {
    tmp <- add_dimension(tmp,
      dim = 3.1, add = "scenario",
      nm = params$gdxPathNames[[i]]
    )
  } else {
    tmp <- add_dimension(tmp,
      dim = 3.1, add = "scenario",
      nm = gsub("\\.", "_", rev(setdiff(
        strsplit(yamlParams$gdxPaths[[i]], "/|\\\\")[[1]], ""
      ))[2])
    )
  }
  data <- mbind(data, tmp)
}

allYears <- getYears(data, as.integer = TRUE)

yearsUntil2050 <- getYears(data, as.integer = TRUE)[
  getYears(data, as.integer = TRUE) <= 2050
]

regionsH12 <- toolGetMapping(name = "regionmappingH12.csv", type = "regional")
regionsH12 <- unique(regionsH12$RegionCode)

regionsEU <- toolGetMapping(name = "regionmapping_21_EU11.csv", type = "regional")
regionsEU <- setdiff(unique(regionsEU$RegionCode), regionsH12)

data <- as.quitte(data) %>% select(region, scenario, variable = all_in, period, value)

.plot <- function(v, y, r) {
  df <- data %>% filter(period %in% y, variable == v, region %in% r)

  p <- ggplot() +
    geom_line(
      data = df,
      aes(x = period, y = value, color = scenario), linewidth = 1
    ) +
    facet_wrap("region", scales = "free_y", ncol = 4) +
    theme_minimal() +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.title = element_blank(),
      legend.position = "bottom"
    ) +
    ggtitle(v) +
    scale_color_brewer(palette = "Set1") +
    expand_limits(y = 0)
  return(p)
}
```

# Results {.tabset .tabset-dropdown}

## Years until 2050 {.tabset} 

### Top Level
```{r top-2050}
vars <- c("inco", "lab", "kap")

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsEU)
    print(p)
  }
}
```


### Buildings
```{r buildings-2050}
vars <- c("feelcb", "fehob", "fesob", "feelhpb", "feelrhb", "feheb", "fegab", "feh2b")

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsEU)
    print(p)
  }
}
```

### Transportation
```{r transportation-2050}
vars <- c("entrp_pass_sm", "entrp_pass_lo", "entrp_frgt_sm", "entrp_frgt_lo")

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsEU)
    print(p)
  }
}
```

### Industry
```{r industry-2050}
vars <- c(
  "ue_cement", "feso_cement", "feli_cement", "fega_cement", "feh2_cement",
  "feel_cement", "kap_cement", "ue_chemicals", "feso_chemicals", "feli_chemicals",
  "fega_chemicals", "feh2_chemicals", "feelhth_chemicals", "feelwlth_chemicals",
  "kap_chemicals", "ue_steel_primary", "feso_steel", "feli_steel", "fega_steel",
  "feh2_steel", "feel_steel_primary", "kap_steel_primary", "ue_steel_secondary",
  "kap_steel_secondary", "feel_steel_secondary", "ue_otherInd", "feso_otherInd",
  "feli_otherInd", "fega_otherInd", "feh2_otherInd", "fehe_otherInd",
  "feelhth_otherInd", "feelwlth_otherInd", "kap_otherInd"
)

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, yearsUntil2050, regionsEU)
    print(p)
  }
}
```

## All years {.tabset}

### Top Level
```{r top-all}
vars <- c("inco", "lab", "kap")
for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsEU)
    print(p)
  }
}
```

### Buildings
```{r buildings-all}
vars <- c("feelcb", "fehob", "fesob", "feelhpb", "feelrhb", "feheb", "fegab", "feh2b")

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsEU)
    print(p)
  }

  print(p)
}
```

### Transportation
```{r transportation-all}
vars <- c("entrp_pass_sm", "entrp_pass_lo", "entrp_frgt_sm", "entrp_frgt_lo")

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsEU)
    print(p)
  }
}
```

### Industry
```{r industry-all}
vars <- c(
  "ue_cement", "feso_cement", "feli_cement", "fega_cement", "feh2_cement",
  "feel_cement", "kap_cement", "ue_chemicals", "feso_chemicals",
  "feli_chemicals", "fega_chemicals", "feh2_chemicals", "feelhth_chemicals",
  "feelwlth_chemicals", "kap_chemicals", "ue_steel_primary", "feso_steel",
  "feli_steel", "fega_steel", "feh2_steel", "feel_steel_primary",
  "kap_steel_primary", "ue_steel_secondary", "kap_steel_secondary",
  "feel_steel_secondary", "ue_otherInd", "feso_otherInd", "feli_otherInd",
  "fega_otherInd", "feh2_otherInd", "fehe_otherInd", "feelhth_otherInd",
  "feelwlth_otherInd", "kap_otherInd"
)

for (v in vars) {
  if (any(regionsH12 %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsH12)
    print(p)
  }

  if (any(regionsEU %in% unique(data$region))) {
    p <- .plot(v, allYears, regionsEU)
    print(p)
  }
}
```
