---
title: "REMIND Nash Convergence"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
params:
  gdx: "fulldata.gdx"
  warning: false
  message: false
  figWidth: 7
---


```{r loading_libraries, include=FALSE}
library(knitr) # nolint
library(dplyr) # nolint
library(remind2) # nolint
library(ggplot2) # nolint

knitr::opts_chunk$set(
  echo = FALSE,
  error = TRUE,
  fig.width = params$figWidth,
  message = params$message,
  warning = params$warning
)

```

## Setup
```{r}

m2r <- gdx::readGDX(params$gdx, "module2realisation", restore_zeros = FALSE)
if (m2r[m2r$module == "optimization", "*"] != "nash") {
  print("Warning: this script only supports nash optimizations")
}

adjustSliderAnimation <- function(p) {
  return(list(p[[1]] %>% plotly::animation_opts(frame = 1)))
}
```

## p80_surplus

### Read Data from gdx
```{r p80_surplus___READ}
p80_surplus <- mip::getPlotData("p80_surplus", params$gdx) %>%
  mutate(tall := as.numeric(tall))
str(p80_surplus)
```

### x: time, slider: iter, facet: enty
```{r}
p <- mip::mipIterations(
  plotData = p80_surplus,
  xAxis = "tall", facets = "all_enty", color = NULL, slider = "iteration",
  facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, slider: time, facet: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = filter(p80_surplus, tall > 2005), # for this to work, we starting year must be available for all facets
  xAxis = "iteration", slider = "tall", color = NULL, facets = "all_enty", facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: time, slider: iter, color: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = p80_surplus,
  xAxis = "tall", facets = NULL, color = "all_enty", slider = "iteration"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, facets: time
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = filter(p80_surplus, tall >= 2025),
  returnGgplots = TRUE,
  xAxis = "iteration", facets = "tall", color = NULL, slider = NULL
)

print(p)
```


## trade price: p80_pvp_itr

### Read Data from gdx
```{r p80_pvp_itr___READ}
p80_pvp_itr <- mip::getPlotData("p80_pvp_itr", params$gdx) %>%
  mutate(ttot := as.numeric(ttot)) %>%
  filter(ttot >= 2005)
str(p80_pvp_itr)
```


### x: time, slider: iter, facet: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = p80_pvp_itr,
  xAxis = "ttot", facets = "all_enty", color = NULL, slider = "iteration",
  facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, slider: time, facet: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  filter(p80_pvp_itr, ttot > 2005), # for this to work, we starting year must be available for all facets
  xAxis = "iteration", slider = "ttot", color = NULL, facets = "all_enty", facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: time, slider: iter, color: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = p80_pvp_itr,
  xAxis = "ttot", facets = NULL, color = "all_enty", slider = "iteration"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, facets: time
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = filter(p80_pvp_itr, ttot >= 2025),
  returnGgplots = TRUE,
  xAxis = "iteration", facets = "ttot", color = NULL, slider = NULL,
  facetScales = "free_y"
)

print(p)
```

## price not discounted

### Read Data from gdx
```{r results = "asis"}
price_not_discounted_itr <- left_join(p80_pvp_itr,
  filter(p80_pvp_itr, all_enty == "good"),
  by = c("ttot", "iteration")
) %>%
  mutate(
    all_enty = all_enty.x,
    p80_pvp_itr_no_discount = p80_pvp_itr.x / p80_pvp_itr.y
  ) %>%
  select("ttot", "iteration", "all_enty", "p80_pvp_itr_no_discount")
```

### x: time, slider: iter, facet: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = price_not_discounted_itr,
  xAxis = "ttot", facets = "all_enty", color = NULL, slider = "iteration",
  facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, slider: time, facet: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  filter(price_not_discounted_itr, ttot > 2005), # for this to work, we starting year must be available for all facets
  xAxis = "iteration", slider = "ttot", color = NULL, facets = "all_enty", facetScales = "free_y"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: time, slider: iter, color: enty
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = price_not_discounted_itr,
  xAxis = "ttot", facets = NULL, color = "all_enty", slider = "iteration"
) %>% adjustSliderAnimation()

htmltools::tagList(p)
```

### x: iter, facets: time
```{r  results = "asis"}
p <- mip::mipIterations(
  plotData = filter(price_not_discounted_itr, ttot >= 2025),
  returnGgplots = TRUE,
  xAxis = "iteration", facets = "ttot", color = NULL, slider = NULL,
  facetScales = "free_y"
)

print(p)
```

## prices and surplus in one plot

### Read Data from gdx
```{r  results = "asis"}
prices_and_surplus <- left_join(p80_surplus, price_not_discounted_itr,
  by = c("tall" = "ttot", "all_enty", "iteration")
) %>%
  filter(!is.na(p80_pvp_itr_no_discount)) %>%
  reshape2::melt(id.vars = c(1, 2, 3))

# calculate iteration +1 and +2

.step <- function(data, i) {
  data %>%
    filter(.data$iteration > i) %>%
    mutate(
      "iteration" := .data$iteration - i,
      "variable" := paste0(.data$variable, "iter+", i)
    ) %>%
    return()
}

prices_and_surplus_steps <- rbind(
  prices_and_surplus,
  .step(prices_and_surplus, 1),
  .step(prices_and_surplus, 2)
) %>%
  mutate(
    "group" = ifelse(grepl("^p80_surplus", .data$variable), "p80_surplus", "p80_pvp_itr_no_discount"),
    "step" = gsub("^(p80_surplus|p80_pvp_itr_no_discount) ?", "", .data$variable),
    "step" = ifelse(.data$step == "", "iter", .data$step)
  ) %>%
  relocate(where(is.numeric), .after = last_col()) %>%
  select(-"variable")
```

### x: time, slider: iter, facet: var
```{r  results = "asis"}
for (v in unique(prices_and_surplus_steps$all_enty)) {
  p <- mip::mipIterations(
    plotData = filter(prices_and_surplus_steps, all_enty == v, tall >= 2005),
    xAxis = "tall", facets = "group", color = "step", slider = "iteration", facetScales = "free_y"
  ) %>% adjustSliderAnimation()

  print(htmltools::tagList(p))
}
```

### x: iter, slider: time, facet: var
```{r  results = "asis"}
for (v in unique(prices_and_surplus$all_enty)) {
  p <- mip::mipIterations(
    plotData = filter(prices_and_surplus, all_enty == v, tall >= 2025),
    xAxis = "iteration", facets = "variable", color = NULL, slider = "tall", facetScales = "free_y"
  ) %>% adjustSliderAnimation()

  print(htmltools::tagList(p))
}
```

### x: iter, facet: time, color: var
```{r  results = "asis", fig.width=12, fig.height=5}
prices_and_surplus_scaled <- left_join(p80_surplus, price_not_discounted_itr,
  by = c("tall" = "ttot", "all_enty", "iteration")
) %>%
  filter(!is.na(p80_pvp_itr_no_discount), tall >= 2025)

for (v in unique(prices_and_surplus_scaled$all_enty)) {
  df <- prices_and_surplus_scaled %>%
    filter(all_enty == v)

  # scale factor per all_enty value
  scale_factor <- round(select(df, "p80_surplus") %>% max() /
                          select(df, "p80_pvp_itr_no_discount") %>% max(), digits = 1)

  df <- df %>%
    mutate(p80_pvp_itr_no_discount := p80_pvp_itr_no_discount * scale_factor) %>%
    reshape2::melt(id.vars = c(1, 2, 3))

  p <- mip::mipIterations(
    plotData = df, returnGgplots = TRUE,
    xAxis = "iteration", facets = "tall", color = "variable", slider = NULL,
    facetScales = "free_y"
  )

  lapply(p, function(plot) {
    plot <- plot +
      ggplot2::scale_y_continuous("p80_surplus", sec.axis =
                                    ggplot2::sec_axis(~ . / scale_factor, name = "p80_pvp_itr_no_discount"))
    print(plot)
  })
}
```

## Convergence Plots
```{r results = "asis"}
diag <- remind2::plotNashConvergence(gdx = params$gdx)
htmltools::tagList(diag$plot)
htmltools::tagList(diag$tradeDetailPlot)
```

## Price Anticipation Plots

### p80_DevPriceAnticipGlobMax2100Iter

- p80_DevPriceAnticipGlobMax2100Iter(all_enty,iteration)  "Track the 2100 value of p80_DevPriceAnticipGlobMax over iterations. [Unit: trillion Dollar]"
- p80_DevPriceAnticipGlobAllMax2100Iter(iteration)        "Track the 2100 value of p80_DevPriceAnticipGlobAllMax over iterations. [Unit: trillion Dollar]"

```{r results = "asis"}
df <- mip::getPlotData("p80_DevPriceAnticipGlobMax2100Iter", params$gdx)

df.all <- mip::getPlotData("p80_DevPriceAnticipGlobAllMax2100Iter", params$gdx) %>%
  mutate(all_enty = "all") %>%
  rename(p80_DevPriceAnticipGlobMax2100Iter = p80_DevPriceAnticipGlobAllMax2100Iter)

df <- rbind(df, df.all)

p <- mip::mipIterations(
  plotData = df, returnGgplots = TRUE, facetScales = "free_y",
  xAxis = "iteration", facets = "all_enty", color = NULL, slider = NULL
)

# add logarithmic scale
p[[1]] + ggplot2::scale_y_log10()
```


### p80_DevPriceAnticipGlobIter

- p80_DevPriceAnticipGlobIter(ttot,all_enty,iteration)    "Track p80_DevPriceAnticipGlob over iterations. [Unit: trillion Dollar]"

```{r results = "asis"}
df <- mip::getPlotData("p80_DevPriceAnticipGlobIter", params$gdx) %>%
  mutate(ttot := as.numeric(ttot))

p <- mip::mipIterations(
  plotData = df,
  xAxis = "ttot", facets = "all_enty", slider = "iteration",
  facetScales = "free_y", returnGgplots = TRUE
)

# add logarithmic scale and then convert to plotly
plots <- p[[1]] + ggplot2::scale_y_log10()
plots <- list(plots)
plots <- lapply(plots, plotly::ggplotly) %>% adjustSliderAnimation()

print(htmltools::tagList(plots))
```


### p80_PriceChangePriceAnticipReg

- p80_PriceChangePriceAnticipReg(ttot,all_enty,all_regi)  "Price change of a trade good due to the price anticipation effect. [Unit: Percent]"

```{r results = "asis"}
df <- mip::getPlotData("p80_PriceChangePriceAnticipReg", params$gdx) %>%
  mutate(ttot := as.numeric(ttot)) %>%
  select(-"iteration")

mip::mipIterations(
  plotData = df, returnGgplots = TRUE,
  xAxis = "ttot", facets = "all_regi", color = "all_enty", slider = NULL,
  facetScales = "free_y"
)
```
### p80_DevPriceAnticipReg

- p80_DevPriceAnticipReg(ttot,all_enty,all_regi)          "Deviation of the yearly monetary export/import expenditure due to price change anticipation effect. [Unit: trillion Dollar]"

```{r results = "asis"}
df <- mip::getPlotData("p80_DevPriceAnticipReg", params$gdx) %>%
  mutate(ttot := as.numeric(ttot)) %>%
  select(-"iteration")

mip::mipIterations(
  plotData = df, returnGgplots = TRUE,
  xAxis = "ttot", facets = "all_regi", color = "all_enty", slider = NULL,
  facetScales = "free_y"
)
```

### p80_DevPriceAnticipGlob
- p80_DevPriceAnticipGlob(ttot,all_enty)                  "Global sum of p80_DevPriceAnticipReg. [Unit: trillion Dollar]"
- p80_DevPriceAnticipGlobAll(ttot)                        "p80_DevPriceAnticipGlob summed over all trade goods. [Units: trillion Dollar]"
- p80_DevPriceAnticipGlobAllMax(ttot)                     "Max of p80_DevPriceAnticipGlobAll until the given year. [Unit: trillion Dollar]"
- p80_DevPriceAnticipGlobMax(ttot,all_enty)               "Max of p80_DevPriceAnticipGlob until the given year. [Unit: trillion Dollar]"

```{r results = "asis"}
df <- mip::getPlotData("p80_DevPriceAnticipGlob", params$gdx) %>%
  mutate(ttot := as.numeric(ttot)) %>%
  select(-"iteration")

df.all <- mip::getPlotData("p80_DevPriceAnticipGlobAll", params$gdx) %>%
  mutate(ttot := as.numeric(ttot), all_enty = "all") %>%
  rename(p80_DevPriceAnticipGlob = p80_DevPriceAnticipGlobAll) %>%
  select(-"iteration")

df.allmax <- mip::getPlotData("p80_DevPriceAnticipGlobAllMax", params$gdx) %>%
  mutate(ttot := as.numeric(ttot), all_enty = "allmax") %>%
  rename(p80_DevPriceAnticipGlob = p80_DevPriceAnticipGlobAllMax) %>%
  select(-"iteration")

df <- rbind(df, df.all, df.allmax)

mip::mipIterations(
  plotData = df, returnGgplots = TRUE,
  xAxis = "ttot", facets = "all_enty", color = NULL, slider = NULL,
  facetScales = "free_y"
)

df.max <- mip::getPlotData("p80_DevPriceAnticipGlobMax", params$gdx) %>%
  select(-"iteration")

mip::mipIterations(
  plotData = df.max, returnGgplots = TRUE,
  xAxis = "ttot", facets = "all_enty", color = NULL, slider = NULL,
  facetScales = "free_y"
)
```
